### 2018-07-28 paper.tex
1.5 models and some writing

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\DeclareMathOperator{\Dist}{Dist}
\DeclareMathOperator{\ctrl}{ctrl}
\DeclareMathOperator{\prnt}{prnt}
\DeclareMathOperator{\link}{link}

\lstdefinelanguage{Big}{
  sensitive=true,
  morekeywords={fun, brs, end, sbrs, pbrs, nbrs, begin, init, atomic, preds,
    rules, action, big, ctrl, float, int, react},
  comment=[l]{\#}
}

\begin{document}
\title{Nondeterministic Bigraphical Reactive Systems for Markov Decision
  Processes\thanks{Supported by organization x.}}
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
\author{Paulius Dilkas\orcidID{0000-1111-2222-3333} \and
  Michele Sevegnani\orcidID{1111-2222-3333-4444}}
\authorrunning{P. Dilkas \& M. Sevegnani}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Glasgow, Glasgow, UK}
\maketitle

\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}

\section{Introduction}

\begin{definition}[\cite{DBLP:conf/nfm/GiaquintaHIMN18}]
  For any finite set $X$, let $\Dist(X)$ denote the set of discrete probability
  distributions over $X$. A \emph{Markov Decision Process} is a tuple $ (S,
  \overline{s}, A, P, L)$, where: $S$ is a finite set of states and
  $\overline{s} \in S$ is the initial state; $A$ is a finite set of
  \emph{actions}; $P : S \times A \to \Dist(S)$ is a (partial) probabilistic
  transition function, mapping state-action pairs to probability distributions
  over $S$; $L : S \to 2^P$ is a labelling with atomic propositions.
\end{definition}

\begin{definition}
  A \emph{reward structure} for an MDP $(S, \overline{s}, A, P, L)$ is a pair
  $(\rho, \iota)$, where $\rho : S \to \mathbb{R}$ is the \emph{state reward
    function}, and $\iota : S \times A \to \mathbb{R}$ is the \emph{transition
    reward function}.
\end{definition}

% TODO rephrase
\begin{definition}
  A \emph{bigraph} is a tuple $(V, E, \ctrl, \prnt, \link) : \langle k, X
  \rangle \to \langle m, Y \rangle$, where $V$ is a set of nodes, $E$ is a set
  of edges, $\ctrl$ is the \emph{control map} that assigns controls to nodes,
  $\prnt$ is the \emph{parent map} that defines the nesting of nodes, and
  $\link$ is the \emph{link map} that defines the link structure.

  The notation $\langle k, X \rangle \to \langle m, Y \rangle$ indicates that
  the bigraph has $k$ \emph{holes} (sites) and a set of inner names $X$ and $m$
  \emph{regions}, with a set of \emph{outer names} $Y$. These are respectively
  known as the \emph{inner} and \emph{outer} interfaces of the bigraph.
\end{definition}

Reaction rule definition \cite{DBLP:journals/corr/abs-1111-0086}

Stochastic bigraphs \cite{DBLP:journals/entcs/KrivineMT08}

PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}

Define NBRS

Lemma: any MDP can be expressed as an NBRS

Changes from PBRS: each reaction rule annotated with an action name
(probabilities normalised over each action separately) and an integer
reward/cost, predicates get a reward/cost, too.

\section{Example}

\begin{figure}
  \includegraphics{models/example_ts.pdf}
  \caption{...}
  \label{example_ts}
\end{figure}

\lstinputlisting[caption=asdf, language=Big]{models/example.big}

\begin{example}
  Consider an MDP $(S, \overline{s}, A, P, L)$, where...
  Look at Figure~\ref{example_ts}.
\end{example}

\section{Exporting to PRISM}

Transitions, state rewards, transition rewards

\section{Case study in autonomous agents}

\bibliographystyle{splncs04}
\bibliography{bibliography}
\end{document}

### 2018-08-03 paper.tex
Main definitions

@@
 \usepackage{amsfonts}
+\usepackage{mathtools}
 \usepackage{color}
@@
 \usepackage{listings}
+\usepackage{wasysym}
 % If you use the hyperref package, please uncomment the following line
@@
 
-\DeclareMathOperator{\Dist}{Dist}
-\DeclareMathOperator{\ctrl}{ctrl}
-\DeclareMathOperator{\prnt}{prnt}
-\DeclareMathOperator{\link}{link}
+\newcommand\Dist{\mathit{Dist}}
+\newcommand\ctrl{\mathit{ctrl}}
+\newcommand\prnt{\mathit{prnt}}
+\newcommand\link{\mathit{link}}
+\newcommand\points{\mathit{points}}
+\newcommand\ports{\mathit{ports}}
+\newcommand\ar{\mathit{ar}}
+\newcommand\id{\mathsf{id}}
+\newcommand\Id{\mathsf{Id}}
+
+\providecommand\longrightarrowRHD{\relbar\joinrel\relbar\joinrel\mathrel\RHD}
+\providecommand\longrightarrowrhd{\relbar\joinrel\relbar\joinrel\mathrel\rhd}
+
+\makeatletter
+\providecommand*\xrightarrowRHD[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longrightarrowRHD}{#1}{#2}}
+\providecommand*\xrightarrowrhd[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longrightarrowrhd}{#1}{#2}}
+\makeatother
 
@@
 
-% TODO rephrase
-\begin{definition}
-  A \emph{bigraph} is a tuple $(V, E, \ctrl, \prnt, \link) : \langle k, X
-  \rangle \to \langle m, Y \rangle$, where $V$ is a set of nodes, $E$ is a set
-  of edges, $\ctrl$ is the \emph{control map} that assigns controls to nodes,
-  $\prnt$ is the \emph{parent map} that defines the nesting of nodes, and
-  $\link$ is the \emph{link map} that defines the link structure.
+From \cite{dblp:journals/tcs/sevegnanic15}.
 
-  The notation $\langle k, X \rangle \to \langle m, Y \rangle$ indicates that
-  the bigraph has $k$ \emph{holes} (sites) and a set of inner names $X$ and $m$
-  \emph{regions}, with a set of \emph{outer names} $Y$. These are respectively
-  known as the \emph{inner} and \emph{outer} interfaces of the bigraph.
+\begin{definition}[Concrete place graph with sharing]
+  A \emph{concrete place graph with sharing}
+  \[ F = (V_F, \ctrl_F, \prnt_F) : m \to n \]
+  is a triple having an inner interface $m$ and an outer interface $n$. These
+  index the sites and regions of the place graph, respectively. $F$ has a finite
+  set $V_F \subset \mathcal{V}$ of nodes, a control map $\ctrl_F : V_F \to
+  \mathcal{K}$, and a \emph{parent relation}
+  \[ \prnt_F \subseteq (m \uplus V_F) \times (V_F \uplus n) \]
+  that is acyclic, i.e., $(v, v) \not\in \prnt_F^+$ for any $v \in V_F$.
 \end{definition}
 
-Reaction rule definition \cite{DBLP:journals/corr/abs-1111-0086}
+\begin{definition}[Composition for place graphs with sharing]
+  If $F : k \to m$ and $G : m \to n$ are two concrete place graphs with sharing
+  with $V_F \cap V_G = \emptyset$, their composite
+  \[ G \circ F = (V, \ctrl, \prnt) : k \to n \]
+  has nodes $V = V_F \uplus V_G$ and control map $\ctrl = \ctrl_F \uplus
+  \ctrl_G$. Its parent relation $\prnt \subseteq (k \uplus V) \times (V \uplus
+  n)$ is given by:
+  \[ \prnt \coloneqq \prnt_G^\lhd \uplus \prnt_\circ \uplus \prnt_F^\rhd, \]
+  where
+  \begin{align*}
+    \prnt_F^\rhd &= \prnt_F \rhd V_F, \\
+    \prnt_G^\lhd &= V_G \lhd \prnt_G, \\
+    \prnt_\circ &= (m \lhd \prnt_G) \circ (\prnt_F \rhd m).
+  \end{align*}
+\end{definition}
+
+\begin{definition}[Tensor product for place graphs]
+  If $G_0 : m_0 \to n_0$ and $G_1 : m_1 \to n_1$ are two concrete place graphs
+  with sharing with $V_F \cap V_G = \emptyset$, their tensor product
+  \[ G_0 \otimes G_1 = (V, \ctrl, \prnt) : m_0 + m_1 \to n_0 + n_1 \]
+  has nodes $V = V_{G_0} \uplus V_{G_1}$ and control map $\ctrl \coloneqq
+  \ctrl_{G_0} \uplus \ctrl_{G_1}$. Its parent relation $\prnt \subseteq [(m_0 +
+  m_1) \uplus V] \times [V \uplus (n_0 + n_1)]$ is defined as
+  \[ \prnt_{G_0} \uplus \prnt_{G_1}^{(m_0, n_0)}, \]
+  where
+  \begin{align*}
+    \prnt_{G_1}^{(m_0, n_0)} = &\{ (v, w) \mid (v, w) \in \prnt_{G_1} \text{ and } v, w \in V_{G_1} \} \\
+    \uplus &\{ (m_0 + i, w) \mid (i, w) \in \prnt_{G_1}, w \in V_{G_1} \text{ and } i \in m_1 \} \\
+    \uplus &\{ (v, n_0 + i) \mid (v, i) \in \prnt_{G_1}, v \in V_{G_1} \text{ and } i \in n_1 \} \\
+    \uplus &\{ (m_0 + i, n_0 + j) \mid (i, j) \in \prnt_{G_1}, i \in m_1, \text{ and } j \in n_1 \}.
+  \end{align*}
+\end{definition}
+
+\begin{definition}[Concrete link graph]
+  A \emph{concrete link graph}
+  \[ F = (V_F, E_F, \ctrl_F, \link_F) : X \to Y \]
+  is a quadruple having an inner face $X$ and an outer face $Y$, both finite
+  subsets of $\mathcal{X}$, called respectivelly the inner and outer names of
+  the link graph. $F$ has finite sets $V_F \subset \mathcal{V}$ of nodes and
+  $E_F \subset \mathcal{E}$ of edges, a control map $\ctrl_F : V_F \to
+  \mathcal{K}$ and a \emph{link map}
+  \[ \link_F : X \uplus P_F \to E_F \uplus Y, \]
+  where $P_F \coloneqq \{ (v, i) \mid i \in \ar(\ctrl_F(v)) \}$ is the set of
+  ports of $F$. Thus $(v, i)$ is the $i$th port of node $v$. We shall call $X
+  \uplus P_F$ the \emph{points} of $F$, and $E_F \uplus Y$ its \emph{links}.
+\end{definition}
+
+The sets of points and the set of ports of a link $l$ are defined by
+\[ \points_F(l) \coloneqq \{ p \mid \link_F(p) = l \}, \quad \ports_F(l)
+  \coloneqq \points_F(l) \setminus X. \]
+An edge is \emph{idle} if it has no points. Identities over name sets are
+defined by $\id_X = (\emptyset, \emptyset, \emptyset, \Id_X) : X \to X$.
+
+\begin{definition}[Concrete bigraph with sharing]
+  A concrete bigraph
+  \[ F = (V_F, E_F, \ctrl_F, \prnt_F, \link_F) : \langle k, X \rangle \to
+    \langle m, Y \rangle \]
+  consists of a concrete place graph with sharing $F^P = (V_F, \ctrl_F, \prnt_F)
+  : k \to m$ and a concrete link graph $F^L = (V_F, E_F, \ctrl_F, \link_F) : X
+  \to Y$. We write the concrete bigraph with sharing as $F = (F^P, F^L)$.
+\end{definition}
+
+Definitions: support translation, lean-support equivalence, concretion,
+abstraction.
+
+More definitions: level, normalised levels, occurrence, matching, concrete
+occurrence, underlying graph
 
@@
 
-PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}
+From PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}
+
+% TODO: not general enough
+\begin{definition}[reaction rule]
+  A \emph{reaction rule} is a pair
+  \[ \mathsf{R} = (R : m \to J, R' : m \to J), \]
+  sometimes written as $R \longrightarrowRHD R'$, where $R$ is the \emph{redex}
+  and $R'$ the \emph{reactum}, and $R$ is solid. The rule generates all the
+  \emph{ground reaction rules} $(r, r')$, where $r = (R \otimes \id_Y) \circ d$
+  and $r' = (R' \otimes \id_Y) \circ d$ for some discrete ground
+  \emph{parameter} $d : \epsilon \to \langle m, Y \rangle$. The \emph{reaction
+    relation} $\longrightarrowrhd_{\mathsf{R}}$ over ground bigraphs is defined
+  by
+  \[ g \longrightarrowrhd_{\mathsf{R}} g' \text{ iff } g = Dr \text{ and } g' = Dr' \]
+  for some bigraph $D$ and some ground reaction rule $(r, r')$ generated from
+  $\mathsf{R}$.
+\end{definition}
+
+\begin{definition}[bigraphical reactive system (BRS)]
+  A \emph{bigraphical reactive system} consists of a pair $(\mathcal{B},
+  \mathcal{R})$, where $\mathcal{B}$ is a set of agents and $\mathcal{R}$ is a
+  set of reaction rules defined over $\mathcal{B}$. It has a reaction relation
+  \[ \longrightarrowrhd_{\mathcal{R}} \coloneqq \bigcup_{\mathsf{R} \in
+      \mathcal{R}} \longrightarrowrhd_{\mathsf{R}}, \]
+  which will be written $\longrightarrowrhd$ when $\mathcal{R}$ is understood.
+  We write $(\mathcal{B}(\Sigma), \mathcal{R})$ when the elements of
+  $\mathcal{B}$ are $\Sigma$-sorted.
+\end{definition}
+
+\subsection{New stuff}
+
+% probabilities sum to 1!
+\begin{definition}[probabilistic reaction rule]
+  A \emph{probabilistic reaction rule} $\mathsf{R}$ is a triple $(R, R', p)$,
+  sometimes written $R \xrightarrowRHD{p} R'$, where $(R, R')$ is a reaction
+  rule and $p \in [0, 1]$ is a probability.
+\end{definition}
 
@@
 
-\section{Example}
+\section{Jupyter interface \& visualisations}
+
+We introduce a convenient graphical user interface for working with bigraphs via
+Jupyter notebooks.
+
+\begin{example} \label{example}
+  Consider an MDP $(S, \overline{s}, A, P, L)$, where...
+  Look at Figure~\ref{example_ts}.
+\end{example}
 
@@
   \includegraphics{models/example_ts.pdf}
-  \caption{...}
+  \caption{The full transition system of Example~\ref{example}.}
   \label{example_ts}
@@
 
-\lstinputlisting[caption=asdf, language=Big]{models/example.big}
+\begin{figure}
+  \includegraphics{images/interface.jpg}
+  \caption{The BigraphER Jupyter interface with syntax highlighting.}
+  \label{interface}
+\end{figure}
 
-\begin{example}
-  Consider an MDP $(S, \overline{s}, A, P, L)$, where...
-  Look at Figure~\ref{example_ts}.
-\end{example}
+\begin{figure}
+  \includegraphics{images/transitions.jpg}
+  \caption{...}
+  \label{transitions}
+\end{figure}
+
+\begin{figure}
+  \includegraphics{images/simulation.jpg}
+  \caption{...}
+  \label{simulation}
+\end{figure}
+
+\begin{figure}
+  \includegraphics{images/output.jpg}
+  \caption{...}
+  \label{output}
+\end{figure}
+
+\lstinputlisting[caption=..., language=Big]{models/example.big}
 

### 2018-08-04 paper.tex
My own definitions

@@
 
-\begin{definition}[\cite{DBLP:conf/nfm/GiaquintaHIMN18}]
+\begin{definition}[Markov decision process] \label{mdp}
   For any finite set $X$, let $\Dist(X)$ denote the set of discrete probability
@@
 
-\begin{definition}
+\begin{definition}[rewards]
   A \emph{reward structure} for an MDP $(S, \overline{s}, A, P, L)$ is a pair
@@
 
-\begin{definition}[Concrete place graph with sharing]
+\begin{definition}[concrete place graph with sharing]
   A \emph{concrete place graph with sharing}
@@
 
-\begin{definition}[Composition for place graphs with sharing]
+\begin{definition}[composition for place graphs with sharing]
   If $F : k \to m$ and $G : m \to n$ are two concrete place graphs with sharing
@@
 
-\begin{definition}[Tensor product for place graphs]
+\begin{definition}[tensor product for place graphs]
   If $G_0 : m_0 \to n_0$ and $G_1 : m_1 \to n_1$ are two concrete place graphs
@@
 
-\begin{definition}[Concrete link graph]
+\begin{definition}[concrete link graph]
   A \emph{concrete link graph}
@@
 
-\begin{definition}[Concrete bigraph with sharing]
+\begin{definition}[concrete bigraph with sharing]
   A concrete bigraph
@@
   : k \to m$ and a concrete link graph $F^L = (V_F, E_F, \ctrl_F, \link_F) : X
-  \to Y$. We write the concrete bigraph with sharing as $F = (F^P, F^L)$.
+  \to Y$. If $X = \epsilon$, then $F$ is called \emph{ground}. We write the
+  concrete bigraph with sharing as $F = (F^P, F^L)$.
 \end{definition}
@@
 % TODO: not general enough
-\begin{definition}[reaction rule]
+\begin{definition}[reaction rule] \label{reaction_rule}
   A \emph{reaction rule} is a pair
@@
   which will be written $\longrightarrowrhd$ when $\mathcal{R}$ is understood.
-  We write $(\mathcal{B}(\Sigma), \mathcal{R})$ when the elements of
-  $\mathcal{B}$ are $\Sigma$-sorted.
 \end{definition}
 
-\subsection{New stuff}
+\subsection{Probabilistic bigraphs}
 
-% probabilities sum to 1!
 \begin{definition}[probabilistic reaction rule]
@@
   sometimes written $R \xrightarrowRHD{p} R'$, where $(R, R')$ is a reaction
-  rule and $p \in [0, 1]$ is a probability.
+  rule and $p \in (0, 1]$ is a probability. Similarly to
+  Definition~\ref{reaction_rule}, it generates a set of ground reaction rules of
+  the form $(r, r', p)$.
 \end{definition}
 
-Define NBRS
+\begin{definition}[probabilistic bigraphical reactive system (PBRS)]
+  A \emph{probabilistic bigraphical reactive system} consists of a pair
+  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of agents and
+  $\mathcal{R}$ is a set of probabilistic reaction rules defined over
+  $\mathcal{B}$.
 
-Lemma: any MDP can be expressed as an NBRS
+  Let $g, g'$ be ground bigraphs, and $\{ (r_i, r'_i, p_i) \}_{i=1}^n$ a set of
+  ground probabilistic reaction rules, where for each $r_i$, there exists a
+  bigraph $D_i$ such that $g = D_ir_i$. Let $S = \{ (r_i, r'_i, p_i) \mid g' =
+  D_ir'_i \}$ (for the same $D_i$), and
+  \[ s = \sum_{i=1}^n p_i. \]
+  Then the reaction relation is defined as
+  \[ g \xrightarrowrhd{p}_{\mathcal{R}} g' \text{ iff } S \ne \emptyset, \]
+  where
+  \[ p = \frac{1}{s}\sum_{(r, r', p') \in S} p'. \]
+\end{definition}
 
-Changes from PBRS: each reaction rule annotated with an action name
-(probabilities normalised over each action separately) and an integer
-reward/cost, predicates get a reward/cost, too.
+\subsection{Nondeterministic bigraphs}
+
+\begin{definition}[nondeterministic reaction rule]
+  Let $A$ be a set of actions. A \emph{nondeterministic reaction rule}
+  $\mathsf{R}$ is a tuple $(R, R', a, p)$, where $(R, R', p)$ is a probabilistic
+  reaction rule, and $a \in A$ is an action. We also define a \emph{reaction
+    reward function} $r : A \to \mathbb{R}$ that assigns a reward/cost to each
+  action.
+\end{definition}
+
+\begin{definition}[nondeterministic bigraphical reactive system (NBRS)]
+  A \emph{nondeterministic bigraphical reactive system} consists of a pair
+  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of agents and
+  $\mathcal{R}$ is a set of nondeterministic reaction rules defined over
+  $\mathcal{B}$.
+
+  Let $g, g'$ be ground bigraphs, $a \in A$ an action, and $\{ (r_i, r'_i, a,
+  p_i) \}_{i=1}^n$ a set of ground nondeterministic reaction rules with action
+  $a$, where for each $r_i$, there exists a bigraph $D_i$ such that $g =
+  D_ir_i$. Let $S = \{ (r_i, r'_i, a, p_i) \mid g' = D_ir'_i \}$ (for the same
+  $D_i$), and
+  \[ s = \sum_{i=1}^n p_i. \]
+  Then the reaction relation for action $a$ is defined as
+  \[ g \xrightarrowrhd[r(a)]{p}_{a} g' \text{ iff } S \ne \emptyset, \]
+  where
+  \[ p = \frac{1}{s}\sum_{(r, r', a, p') \in S} p'. \]
+\end{definition}
+
+% TODO: states
+BigraphER \cite{DBLP:conf/cav/SevegnaniC16} supports defining predicates, i.e.,
+bigraphs that are compared to every encountered state. We can associate a reward
+with each predicate, allowing us to assign rewards to states in a flexible and
+semantically meaningful way: the reward of a state is simply the sum of the
+rewards of all matching predicates (and $0$ in case there are none).
+
+\begin{proposition}
+  Any MDP can be expressed as an NBRS.
+\end{proposition}
+\begin{proof}
+  Obvious.
+\end{proof}
 
@@
 \begin{example} \label{example}
-  Consider an MDP $(S, \overline{s}, A, P, L)$, where...
-  Look at Figure~\ref{example_ts}.
+  Consider an MDP $(S, \overline{s}, A, P, L)$, where $S = \{ s_0, s_1, s_2, s_3
+  \}$, $\overline{s} = s_0$, $A = \{ a, b, c \}$, and $P, L$ defined as follows:
+  \begin{equation*}
+    \begin{split}
+      P(s_0, a) &= [s_1 \mapsto 1], \\
+      P(s_1, b) &= [s_0 \mapsto 0.7, s_1 \mapsto 0.3], \\
+      P(s_1, c) &= [s_2 \mapsto 0.5, s_3 \mapsto 0.5], \\
+      P(s_2, a) &= [s_2 \mapsto 1], \\
+      P(s_3, a) &= [s_3 \mapsto 1],
+    \end{split}
+    \qquad
+    \begin{split}
+      L(s_0) &= \{ initial \}, \\
+      L(s_1) &= \emptyset, \\
+      L(s_2) &= \{ heads \}, \\
+      L(s_3) &= \{ tails \}.
+    \end{split}
+  \end{equation*}
+  Furthermore, equip it with a reward structure $(\rho, \iota)$, where
+  $\rho(s_2) = 3$, $\iota(s_1, b) = 1$, and both functions are zero everywhere
+  else.
+
+  The MDP can be represented as an NBRS with BigraphER code in Listing
+  \ref{example_listing}. Furthermore, the BigraphER's visualisation of the
+  (automatically generated) transition system is in Fig. \ref{example_ts}.
 \end{example}
@@
 \begin{figure}
+  \begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
+    \begin{minipage}{0.5\textwidth}
+      \vspace{13mm}
+      \lstinputlisting[caption=BigraphER code., captionpos=b, language=Big, label=example_listing]{models/example.big}
+    \end{minipage}
+    &
+      \begin{minipage}{0.5\textwidth}
+        \centering
         \includegraphics{models/example_ts.pdf}
-  \caption{The full transition system of Example~\ref{example}.}
+        \caption{The full transition system.}
         \label{example_ts}
+      \end{minipage}
+  \end{tabular}
 \end{figure}
@@
 
-\lstinputlisting[caption=..., language=Big]{models/example.big}
-
 \section{Exporting to PRISM}

### 2018-08-04 paper.tex
Explanation of the implementation (and cleaning up stuff)

@@
 \usepackage{wasysym}
+\usepackage[lighttt]{lmodern}
 % If you use the hyperref package, please uncomment the following line
@@
 \lstdefinelanguage{Big}{
+  basicstyle=\ttfamily,
   sensitive=true,
@@
   Processes\thanks{Supported by organization x.}}
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-\author{Paulius Dilkas\orcidID{0000-1111-2222-3333} \and
-  Michele Sevegnani\orcidID{1111-2222-3333-4444}}
+\titlerunning{Nondeterministic BRSs for MDPs}
+\author{Paulius Dilkas \and Michele Sevegnani}
 \authorrunning{P. Dilkas \& M. Sevegnani}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
 \institute{University of Glasgow, Glasgow, UK}
@@
 
-\keywords{First keyword \and Second keyword \and Another keyword.}
+\keywords{Bigraphs \and Probabilistic semantics \and Markov decision process.}
 \end{abstract}
@@
 
-Definitions: support translation, lean-support equivalence, concretion,
-abstraction.
-
-More definitions: level, normalised levels, occurrence, matching, concrete
-occurrence, underlying graph
-
-Stochastic bigraphs \cite{DBLP:journals/entcs/KrivineMT08}
-
 From PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}
 
-% TODO: not general enough
 \begin{definition}[reaction rule] \label{reaction_rule}
@@
   A \emph{bigraphical reactive system} consists of a pair $(\mathcal{B},
-  \mathcal{R})$, where $\mathcal{B}$ is a set of agents and $\mathcal{R}$ is a
+  \mathcal{R})$, where $\mathcal{B}$ is a set of bigraphs and $\mathcal{R}$ is a
   set of reaction rules defined over $\mathcal{B}$. It has a reaction relation
@@
   A \emph{probabilistic bigraphical reactive system} consists of a pair
-  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of agents and
+  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of bigraphs and
   $\mathcal{R}$ is a set of probabilistic reaction rules defined over
@@
   A \emph{nondeterministic bigraphical reactive system} consists of a pair
-  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of agents and
+  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of bigraphs and
   $\mathcal{R}$ is a set of nondeterministic reaction rules defined over
@@
 
-\section{Jupyter interface \& visualisations}
-
-We introduce a convenient graphical user interface for working with bigraphs via
-Jupyter notebooks.
+\section{Implementation}
 
@@
   else.
-
-  The MDP can be represented as an NBRS with BigraphER code in Listing
-  \ref{example_listing}. Furthermore, the BigraphER's visualisation of the
-  (automatically generated) transition system is in Fig. \ref{example_ts}.
 \end{example}
@@
 \end{figure}
+
+The MDP can be represented as an NBRS with BigraphER code in Listing
+\ref{example_listing}. Furthermore, the BigraphER's visualisation of the
+(automatically generated) transition system is in Fig. \ref{example_ts}.
+
+More specifically, reaction rule probabilities are represented as floating-point
+numbers inside the arrows (e.g. \texttt{-[0.7]->}), each action encompasses its
+reaction rules with \texttt{\textbf{action} actionName} and
+\texttt{\textbf{end}}. Rewards can be added to actions simply by inserting an
+integer enclosed in squared brackets after the action name (e.g.
+\texttt{\textbf{action} b[1]}). Lastly, predicate rewards have the same format,
+but are listed on the \texttt{\textbf{preds}} line of the \texttt{\textbf{begin
+    nbrs}}---\texttt{\textbf{end}} block (e.g. \texttt{\textbf{preds} =
+  \{heads[3]\};}).
+
+Visually, each state is represented by a white ellipse (the starting state is
+highlighted with a thicker border), and each action (per state) is a grey
+ellipse. Text inside state ellipses lists all predicates that are satisfied by
+that state. Edges from actions to states are labelled with both the probability
+and the name of the reaction rule. Transitions from either a fully generated
+transition system or a simulation, labels from predicates, and state/transition
+rewards can be exported to the corresponding PRISM plain text formats.
 
@@
 
-\section{Exporting to PRISM}
-
-Transitions, state rewards, transition rewards
-
 \section{Case study in autonomous agents}

### 2018-08-06 paper.tex
Describing the first agent (almost done)

@@
 
+\ttfamily
+\DeclareFontShape{OT1}{lmtt}{m}{it}
+     {<->sub*lmtt/m/sl}{}
+
 \begin{document}
@@
 
+\subsection{Markov Decision Processes}
+
 \begin{definition}[Markov decision process] \label{mdp}
@@
 
+\subsection{Bigraphs}
+
 From \cite{dblp:journals/tcs/sevegnanic15}.
+From PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}
+
+\begin{figure}
+  \includegraphics{models/example_bigraph/foo_lhs.pdf}
+  \caption{An example bigraph.}
+  \label{example_bigraph}
+\end{figure}
+
+Consider the graphical representation of a bigraph in Fig.
+\ref{example_bigraph}. The two white dashed rectangles represent \emph{regions},
+i.e. parents of any otherwise parentless nodes. Grey dashed rectangles are
+called \emph{sites} and encode parts of the model that have been abstracted
+away. Nodes, sites, and regions are also known as \emph{places}. Two places with
+the same parent, or two points with the same link are called \emph{siblings}.
 
@@
   : k \to m$ and a concrete link graph $F^L = (V_F, E_F, \ctrl_F, \link_F) : X
-  \to Y$. If $X = \epsilon$, then $F$ is called \emph{ground}. We write the
-  concrete bigraph with sharing as $F = (F^P, F^L)$.
+  \to Y$. We write the concrete bigraph with sharing as $F = (F^P, F^L)$.
 \end{definition}
 
-From PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}
+Given a set of reaction rules, we refer to the configurations that a system may
+adopt as \emph{states}. A bigraph with inner face $\epsilon$ is called
+\emph{ground}.
+
+\begin{definition}[solid bigraph]
+  A bigraph is \emph{solid} if these conditions hold:
+  \begin{enumerate}
+  \item no regions or outer names are idle (a region is called \emph{idle}
+    if it is empty);
+  \item no two sites or inner names are siblings;
+  \item the parent of every site is a node;
+  \item no outer name is linked to an inner name.
+  \end{enumerate}
+\end{definition}
 
@@
   by
-  \[ g \longrightarrowrhd_{\mathsf{R}} g' \text{ iff } g = Dr \text{ and } g' = Dr' \]
+  \[ g \longrightarrowrhd_{\mathsf{R}} g' \text{ iff } g = D \circ r \text{ and
+    } g' = D \circ r' \]
   for some bigraph $D$ and some ground reaction rule $(r, r')$ generated from
@@
   A \emph{bigraphical reactive system} consists of a pair $(\mathcal{B},
-  \mathcal{R})$, where $\mathcal{B}$ is a set of bigraphs and $\mathcal{R}$ is a
-  set of reaction rules defined over $\mathcal{B}$. It has a reaction relation
+  \mathcal{R})$, where $\mathcal{B}$ is a set of ground bigraphs and
+  $\mathcal{R}$ is a set of reaction rules defined over $\mathcal{B}$. It has a
+  reaction relation
   \[ \longrightarrowrhd_{\mathcal{R}} \coloneqq \bigcup_{\mathsf{R} \in
@@
 
-\subsection{Probabilistic bigraphs}
+\section{Extensions to Bigraphs}
+
+\subsection{Probabilistic Bigraphs}
 
@@
   A \emph{probabilistic bigraphical reactive system} consists of a pair
-  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of bigraphs and
-  $\mathcal{R}$ is a set of probabilistic reaction rules defined over
+  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of ground bigraphs
+  and $\mathcal{R}$ is a set of probabilistic reaction rules defined over
   $\mathcal{B}$.
@@
 
-\subsection{Nondeterministic bigraphs}
+\subsection{Nondeterministic Bigraphs}
 
@@
   A \emph{nondeterministic bigraphical reactive system} consists of a pair
-  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of bigraphs and
-  $\mathcal{R}$ is a set of nondeterministic reaction rules defined over
+  $(\mathcal{B}, \mathcal{R})$, where $\mathcal{B}$ is a set of ground bigraphs
+  and $\mathcal{R}$ is a set of nondeterministic reaction rules defined over
   $\mathcal{B}$.
@@
 
-% TODO: states
 BigraphER \cite{DBLP:conf/cav/SevegnaniC16} supports defining predicates, i.e.,
@@
 
+% TODO: introduce this
 \begin{figure}
@@
 
-\begin{figure}
-  \includegraphics{images/transitions.jpg}
-  \caption{...}
-  \label{transitions}
-\end{figure}
+\section{A Case Study in Autonomous Agents}
 
-\begin{figure}
-  \includegraphics{images/simulation.jpg}
-  \caption{...}
-  \label{simulation}
-\end{figure}
+Akin to \cite{dblp:conf/nfm/giaquintahimn18}.
 
-\begin{figure}
-  \includegraphics{images/output.jpg}
-  \caption{...}
-  \label{output}
-\end{figure}
+\subsection{\#1}
 
-\section{Case study in autonomous agents}
+Grid layout (but could be any nodes-and-edges layout, as long as it's clear how
+to go back home). Tracking visited/unvisited states. Each unvisited state has a
+probability $p$ of containing an object. The agent returns (and stays) home
+after collecting a set number of objects (easily customisable). Starting at the
+bottom left cell.
+
+\lstinputlisting[caption=Controls., captionpos=b, language=Big,
+label=agent1_controls, firstline=3, lastline=17]{models/agent1.big}
+
+We begin by introducing controls: the types of nodes, what they contain, and
+what they are linked to. The full list of controls is in Listing
+\ref{agent1_controls}. \texttt{Cell} represents a discrete location. It is
+linked to either \texttt{Visited} or \texttt{Unvisited} (initially, all except
+one cells are unvisited). \texttt{Cell}s always contain
+\texttt{Directions}, and one \texttt{Cell} contains an \texttt{Agent}. The
+\texttt{Agent} may contain an \texttt{Object}, which may contain another
+\texttt{Object}, etc. \texttt{Directions} always contain four nodes:
+\texttt{North}, \texttt{East}, \texttt{West}, \texttt{South}. A \texttt{West}
+node can be linked either to one of the two \texttt{Void}s or to an
+\texttt{East} node of a neighbouring \texttt{Cell} (and similarly with other
+directions). \texttt{Void}s represent the edges of the map. Using two
+\texttt{Void} controls prevents us from unintentionally connecting the opposite
+edges of the map. \texttt{Void1} corresponds to top and left edges, while
+\texttt{Void2} is for bottom and right.
+
+\lstinputlisting[caption=Predicates and the initial state., captionpos=b,
+language=Big, label=agent1_code, firstline=19,
+lastline=50]{models/agent1.big}
+
+Next, we define two predicates: \texttt{home} and \texttt{goal} (see Listing
+\ref{agent1_code}). The former states that the \texttt{Agent} is home
+if it is in the southwest corner of the grid,
+while the latter says that the agent should go home as soon as
+it gets one object. A larger number of objects can be set by,
+e.g., \texttt{Agent.Object.Object}. Additionally, Listing \ref{agent1_code}
+defines the initial $2 \times 2$ grid, as described previously.
+
+\lstinputlisting[caption=The action of going \texttt{north}, captionpos=b,
+language=Big, label=agent1_north, firstline=108,
+lastline=141]{models/agent1.big}
+
+Lastly, we have five actions (four for the directions, and one for
+going home). Each of the actions for directions carries three reaction
+rules: one for going to an already visited cell, one for visiting a
+cell for the first time, and one for visiting a cell for the
+first time and finding an object. We will use the rules for going north
+in Listing \ref{agent1_north} as an example. When going to an already visited
+cell, the \texttt{Agent} simply traverses a link between the \texttt{North} node
+of its previous \texttt{Cell} and the corresponding \texttt{South} node. As this
+is the only reaction rule for this situation, its probability is $1$. When
+going to an unvisited node, we equip an \texttt{Object} with probability $p$.
+Regardless of whether that happens or not, the \texttt{Cell} changes its
+status from \texttt{Unvisited} to \texttt{Visited}. % TODO: going home now
+
+\section{Conclusion}
 

### 2018-08-06 paper.tex
Finished description of Agent 1 (but not finished improving it)

@@
 
-\lstinputlisting[caption=The action of going \texttt{north}, captionpos=b,
+\lstinputlisting[caption=The action of going north, captionpos=b,
 language=Big, label=agent1_north, firstline=108,
@@
 Regardless of whether that happens or not, the \texttt{Cell} changes its
-status from \texttt{Unvisited} to \texttt{Visited}. % TODO: going home now
+link from \texttt{Unvisited} to \texttt{Visited}.
+
+\lstinputlisting[caption=Reaction rule to stay home if a required number of
+objects is acquired., captionpos=b, language=Big, label=agent1_home,
+firstline=204, lastline=216]{models/agent1.big}
+
+The action \texttt{home} has five reaction rules: going west/south to a
+visited/unvisited cell that are just like the rules in Listing
+\ref{agent1_north}, except every mention of \texttt{Agent} is replaced with
+\texttt{goal}, and a rule to stay home if the goal is satisfied (in Listing
+\ref{agent1_home}).
 

### 2018-08-06 paper.tex
Agent1 code updated to use node omission instead of Void

@@
 \lstinputlisting[caption=Controls., captionpos=b, language=Big,
-label=agent1_controls, firstline=3, lastline=17]{models/agent1.big}
+label=agent1_controls, firstline=3, lastline=14]{models/agent1.big}
 
@@
 \lstinputlisting[caption=Predicates and the initial state., captionpos=b,
-language=Big, label=agent1_code, firstline=19,
-lastline=50]{models/agent1.big}
+language=Big, label=agent1_code, firstline=16,
+lastline=30]{models/agent1.big}
 
@@
 \lstinputlisting[caption=The action of going north, captionpos=b,
-language=Big, label=agent1_north, firstline=108,
-lastline=141]{models/agent1.big}
+language=Big, label=agent1_north, firstline=88,
+lastline=117]{models/agent1.big}
 
@@
 objects is acquired., captionpos=b, language=Big, label=agent1_home,
-firstline=204, lastline=216]{models/agent1.big}
+firstline=180, lastline=183]{models/agent1.big}
 

### 2018-08-08 paper.tex
Almost acceptable section on Agent 1, and the technical bits of Agent 2

@@
 \providecommand\longrightarrowrhd{\relbar\joinrel\relbar\joinrel\mathrel\rhd}
+\providecommand\longrightdoublearrowRHD{\mathrel\LHD\joinrel\relbar\joinrel\relbar\joinrel\mathrel\RHD}
 
@@
 \titlerunning{Nondeterministic BRSs for MDPs}
-\author{Paulius Dilkas \and Michele Sevegnani}
-\authorrunning{P. Dilkas \& M. Sevegnani}
+\author{Paulius Dilkas}
+\authorrunning{P. Dilkas}
 \institute{University of Glasgow, Glasgow, UK}
@@
 \begin{figure}
+  \centering
   \includegraphics{models/example_bigraph/foo_lhs.pdf}
@@
 Consider the graphical representation of a bigraph in Fig.
-\ref{example_bigraph}. The two white dashed rectangles represent \emph{regions},
+\ref{example_bigraph}. The white ellipses are the \emph{nodes}. Each node has a
+type, called \emph{control}, denoted here by the labels \textsf{A}, \textsf{B},
+and \textsf{C}. The two white dashed rectangles represent \emph{regions},
 i.e. parents of any otherwise parentless nodes. Grey dashed rectangles are
@@
 \begin{figure}
+  \centering
   \begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
     \begin{minipage}{0.5\textwidth}
-      \vspace{13mm}
+      \centering
       \lstinputlisting[caption=BigraphER code., captionpos=b, language=Big, label=example_listing]{models/example.big}
@@
         \centering
-        \includegraphics{models/example_ts.pdf}
+        \vspace{12mm}
+        \includegraphics[width=\textwidth]{models/example_ts.pdf}
         \caption{The full transition system.}
@@
 \begin{figure}
+  \centering
   \includegraphics{images/interface.jpg}
@@
 
-Akin to \cite{dblp:conf/nfm/giaquintahimn18}.
+Akin to \cite{dblp:conf/nfm/giaquintahimn18} and maybe \cite{koenig1998xavier}.
 
-\subsection{\#1}
+\subsection{Collecting Objects in a Grid}
 
+% TODO: what is a link, mention that it's a hyperedge (at least one node)
 Grid layout (but could be any nodes-and-edges layout, as long as it's clear how
@@
 
-We begin by introducing controls: the types of nodes, what they contain, and
-what they are linked to. The full list of controls is in Listing
-\ref{agent1_controls}. \texttt{Cell} represents a discrete location. It is
-linked to either \texttt{Visited} or \texttt{Unvisited} (initially, all except
-one cells are unvisited). \texttt{Cell}s always contain
+We begin with a list of controls in Listing \ref{agent1_controls}. On the right
+hand side of each equal sign is the number of ports that each node of that
+control has, while the \texttt{\textbf{atomic}} keyword specifies the nodes that
+cannot contain other nodes. \texttt{Cell}s represents discrete locations. They
+are linked to either \texttt{Visited} or \texttt{Unvisited} (initially, all
+except one cells are unvisited). \texttt{Cell}s always contain
 \texttt{Directions}, and one \texttt{Cell} contains an \texttt{Agent}. The
-\texttt{Agent} may contain an \texttt{Object}, which may contain another
-\texttt{Object}, etc. \texttt{Directions} always contain four nodes:
-\texttt{North}, \texttt{East}, \texttt{West}, \texttt{South}. A \texttt{West}
-node can be linked either to one of the two \texttt{Void}s or to an
-\texttt{East} node of a neighbouring \texttt{Cell} (and similarly with other
-directions). \texttt{Void}s represent the edges of the map. Using two
-\texttt{Void} controls prevents us from unintentionally connecting the opposite
-edges of the map. \texttt{Void1} corresponds to top and left edges, while
-\texttt{Void2} is for bottom and right.
+\texttt{Agent} may contain an \texttt{Object}. In order to represent multiple
+objects, it is convenient to put the second \texttt{Object} inside the first,
+and so on. \texttt{Directions} contains a subset of the four nodes,
+corresponding to the four possible directions of travel: \texttt{North},
+\texttt{East}, \texttt{West}, \texttt{South}. We connect neighbouring
+\texttt{Cell}s by linking the \texttt{West} node of one \texttt{Cell} to the
+\texttt{East} node of another (or \texttt{North} to \texttt{South}).
 
@@
 Next, we define two predicates: \texttt{home} and \texttt{goal} (see Listing
-\ref{agent1_code}). The former states that the \texttt{Agent} is home
+\ref{agent1_code}). The former states that the agent is home
 if it is in the southwest corner of the grid,
-while the latter says that the agent should go home as soon as
-it gets one object. A larger number of objects can be set by,
-e.g., \texttt{Agent.Object.Object}. Additionally, Listing \ref{agent1_code}
-defines the initial $2 \times 2$ grid, as described previously.
+while the latter specifies a goal of collecting one object. A larger number of
+objects can be set by nesting \texttt{Object}s inside each other, e.g.,
+\texttt{Agent.Object.Object}. Additionally, Listing \ref{agent1_code} defines
+the initial $2 \times 2$ grid, as described previously.
 
-\lstinputlisting[caption=The action of going north, captionpos=b,
+\lstinputlisting[caption=The action of going north., captionpos=b,
 language=Big, label=agent1_north, firstline=88,
@@
 
-Lastly, we have five actions (four for the directions, and one for
-going home). Each of the actions for directions carries three reaction
-rules: one for going to an already visited cell, one for visiting a
-cell for the first time, and one for visiting a cell for the
-first time and finding an object. We will use the rules for going north
-in Listing \ref{agent1_north} as an example. When going to an already visited
-cell, the \texttt{Agent} simply traverses a link between the \texttt{North} node
-of its previous \texttt{Cell} and the corresponding \texttt{South} node. As this
-is the only reaction rule for this situation, its probability is $1$. When
-going to an unvisited node, we equip an \texttt{Object} with probability $p$.
-Regardless of whether that happens or not, the \texttt{Cell} changes its
-link from \texttt{Unvisited} to \texttt{Visited}.
+Then, we have an action for each of the four directions, each with three
+reaction rules: one for going to an already visited cell, one for visiting a
+cell for the first time, and one for visiting a cell for the first time and
+finding an object. We will use the rules for going north in Listing
+\ref{agent1_north} as an example. When going to an already visited cell, the
+\texttt{Agent} simply traverses a link between the \texttt{North} node of its
+previous \texttt{Cell} and the corresponding \texttt{South} node. As this is the
+only reaction rule for this situation, its probability is $1$. When going to an
+unvisited node, we collect an \texttt{Object} with probability $p$, or make the
+transition without getting an \texttt{Object} with probability $1-p$.
+Regardless, the \texttt{Cell} changes its link from \texttt{Unvisited} to
+\texttt{Visited}.
 
@@
 objects is acquired., captionpos=b, language=Big, label=agent1_home,
-firstline=180, lastline=183]{models/agent1.big}
+firstline=186, lastline=189]{models/agent1.big}
 
-The action \texttt{home} has five reaction rules: going west/south to a
-visited/unvisited cell that are just like the rules in Listing
+Lastly, we have three actions for after the agent acquires the specified number
+of objects: two for going home west or south (since these are the two directions
+necessary and sufficient to reach home), and one for staying home. The
+former type of actions have two reaction rules each, depending on whether the
+destination cell is visited or not. They are just like the rules in Listing
 \ref{agent1_north}, except every mention of \texttt{Agent} is replaced with
-\texttt{goal}, and a rule to stay home if the goal is satisfied (in Listing
-\ref{agent1_home}).
+\texttt{goal}. The rule to stay home is quite straightforward and is in
+Listing \ref{agent1_home}.
+
+\subsection{Layers of Abstraction}
+
+\lstinputlisting[caption={The initial map: three consecutive cells, the midmost
+of which has an inner room.}, captionpos=b, language=Big, label=agent2_initial,
+firstline=15, lastline=19]{models/agent2/agent.big}
+
+\lstinputlisting[caption={Two ways to generate a room, leaving one door either
+open or closed.}, captionpos=b, language=Big, label=agent2_room,
+firstline=21, lastline=48]{models/agent2/agent.big}
+
+\begin{figure}
+  \centering
+  \begin{minipage}{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{models/agent2/goIn_lhs.pdf}
+  \end{minipage}
+  $\longrightdoublearrowRHD$
+  \begin{minipage}{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{models/agent2/goIn_rhs.pdf}
+  \end{minipage}
+  \caption{Left to right: the reaction rule to go inside; right to left: the
+    reaction rule to go outside.}
+  \label{go_in_out}
+\end{figure}
 

### 2018-08-09 paper.tex
Mostly done with the case studies

@@
 \usepackage[lighttt]{lmodern}
+\usepackage{siunitx}
 % If you use the hyperref package, please uncomment the following line
@@
 
-\keywords{Bigraphs \and Probabilistic semantics \and Markov decision process.}
+\keywords{Bigraphs \and Bigraphical Reactive Systems \and Probabilistic
+  semantics \and Markov decision process.}
 \end{abstract}
@@
 
+% TODO: introduce bigrapher
 From \cite{dblp:journals/tcs/sevegnanic15}.
@@
 
+Lastly, BigraphER supports \emph{rule priorities}
+\cite{DBLP:journals/tcs/BaetenBKW89}, i.e., a partial ordering on the reaction
+rules, where a rule of lower priority can be applied only if no rule of higher
+priority is applicable. Priorities are implemented by assigning each reaction
+rule to a \emph{priority class}, where all classes are strictly ordered, and
+reaction rules in the same class have the same priority.
+
 \section{Extensions to Bigraphs}
@@
 rewards of all matching predicates (and $0$ in case there are none).
-
-\begin{proposition}
-  Any MDP can be expressed as an NBRS.
-\end{proposition}
-\begin{proof}
-  Obvious.
-\end{proof}
 
@@
 
-Akin to \cite{dblp:conf/nfm/giaquintahimn18} and maybe \cite{koenig1998xavier}.
+% TODO: Akin to \cite{dblp:conf/nfm/giaquintahimn18} and maybe \cite{koenig1998xavier}.
 
@@
 % TODO: what is a link, mention that it's a hyperedge (at least one node)
-Grid layout (but could be any nodes-and-edges layout, as long as it's clear how
-to go back home). Tracking visited/unvisited states. Each unvisited state has a
-probability $p$ of containing an object. The agent returns (and stays) home
-after collecting a set number of objects (easily customisable). Starting at the
-bottom left cell.
+% TODO: explain the syntax of the language
+Our first scenario is concerned with collecting objects in a grid-like
+two-dimensional world. The agent starts in the southwest corner of the map
+(which we call \emph{home}), explores the environment until it collects a
+specified number of objects, and returns home (while possibly collecting more
+objects along the way). The model tracks which cells of the grid have been
+explored, and only the unexplored cells have a constant probability $p$ of
+rewarding the agent with an object. The desired number of objects can be easily
+changed, and the map can be customised to make some transitions unavailable
+(i.e. add walls), as long as the agent can still return home.
 
@@
 
-Lastly, we have three actions for after the agent acquires the specified number
+Lastly, we have three actions for when the agent acquires the specified number
 of objects: two for going home west or south (since these are the two directions
-necessary and sufficient to reach home), and one for staying home. The
-former type of actions have two reaction rules each, depending on whether the
+necessary and sufficient to reach home), and one for staying home. The two
+actions for going home have two reaction rules each, depending on whether the
 destination cell is visited or not. They are just like the rules in Listing
 \ref{agent1_north}, except every mention of \texttt{Agent} is replaced with
-\texttt{goal}. The rule to stay home is quite straightforward and is in
-Listing \ref{agent1_home}.
+\texttt{goal}. The rule to stay home simply says that if the agent has achieved
+the goal, and is home (characterised by a \texttt{Cell} with only two
+directions: \texttt{North} and \texttt{East}), then nothing should change (see
+Listing \ref{agent1_home}). To make the agent start heading home as soon as
+enough objects are collected, all five reaction rules related to going and
+staying home are in a higher priority class.
 
 \subsection{Layers of Abstraction}
+
+% TODO: Must mention: \cite{DBLP:conf/giscience/WaltonW12}.
+
+Our second model explores two important concepts in modelling the topology of
+space: nesting and uncertainty. Nesting is the idea that spaces can be inside
+other spaces: rooms inside floors, floors inside buildings, buildings inside
+streets, etc. A key characteristic of nested spaces is that there is a separate
+action (or several) taking you from the outer space to the inner space or vice
+versa (e.g., using a door to enter or leave a room). In the rest of the paper,
+whenever we discuss one space inside another, we will refer to the inner space
+as the \emph{room}.
+
+The other concept explored in this section is uncertainty about the topology
+itself, i.e., is the door open or closed? The implementation of this idea is
+tied to that of rooms: the inside of a room is not defined until the outer cell
+encompassing the room (i.e., the area where the door is located) is entered.
+Then, the contents of the room are chosen from a finite set of possibilities
+with a set probability distribution. After that, the room stays fixed. This
+design decision supports the reality of missions with a reasonably short
+duration: if the agent finds a locked door, it should not keep revisiting the
+door hoping for it to suddenly be open.
+
+As the ideas of collecting objects and tracking visited cells have been
+explored already, they are dropped from this model to simplify the
+implementation. The goal can simply be defined as moving from one location to
+another. We add one extra control, \texttt{Node}. While \texttt{Cell} can be
+imagined as a discrete patch of space (e.g., \SI{1}{\square\metre}),
+\texttt{Node} can be thought of as a room. While we stick to two layers
+(corridors and rooms) in this example, rooms can be freely nested: a room can
+contain any number of rooms, each of which can contain more rooms.
+
+\begin{figure}
+  \centering
+  \includegraphics{models/agent2/nesting_example/example.pdf}
+  \caption{The bigraphical structure behind nesting.}
+  \label{agent2_nesting}
+\end{figure}
 
@@
 firstline=15, lastline=19]{models/agent2/agent.big}
-
-\lstinputlisting[caption={Two ways to generate a room, leaving one door either
-open or closed.}, captionpos=b, language=Big, label=agent2_room,
-firstline=21, lastline=48]{models/agent2/agent.big}
 
@@
 
+In order to impement nesting, a \texttt{Cell} contains a \texttt{Node}, which
+can have any number of \texttt{Cell}s of its own. Since after entering a room,
+you end up in a specific place inside the room (next to the door), we also need
+to link up the \texttt{Node} with one of the \texttt{Cell}s it contains (see
+Fig. \ref{agent2_nesting}). Both \texttt{Cell}s and \texttt{Node}s support
+having a single link for exactly this purpose. Thus, most of the \texttt{Cell}
+ports are not linked to anything, which is implemented via closures (e.g.
+\texttt{/x Cell\{x\}}). The initial map in Listing \ref{agent2_initial} has a
+corridor of three cells, with the agent on the west-most cell, and a door to a
+room in the middle cell. One moves in and out of a room via a pair of actions
+with reaction rules pictured in Fig. \ref{go_in_out}.
+
+\lstinputlisting[caption={Two ways to generate a room, leaving one door either
+open or closed.}, captionpos=b, language=Big, label=agent2_room,
+firstline=21, lastline=48]{models/agent2/agent.big}
+
+\lstinputlisting[caption={The action of going north.}, captionpos=b,
+language=Big, label=agent2_north, firstline=66,
+lastline=75]{models/agent2/agent.big}
+
+The room is a $2 \times 2$ grid of \texttt{Cell}s, which is generated when the
+\texttt{Agent} gets to a \texttt{Cell} with an empty \texttt{Node} (represented
+by \texttt{Node\{n\}.1}). In order for this to happen before any other action
+can take place, the two reaction rules in Listing \ref{agent2_room} are put on a
+higher priority class. With probability $p$, the generated room has each
+\texttt{Cell} linked to its two neighbours; and with probability $1-p$, the top
+two \texttt{Cell}s are not linked , possibly forcing the agent to choose a
+different path. Finally, we have four actions, each with a single reaction rule
+with probability $1$, corresponding to the four possible directions of travel.
+The reaction rules are very similar to those of our previous example, see
+Listing \ref{agent2_north}.
+
 \section{Conclusion}

### 2018-08-10 paper.tex
Lots of improvements, especially in describing bigraphs

@@
 \newcommand\link{\mathit{link}}
-\newcommand\points{\mathit{points}}
-\newcommand\ports{\mathit{ports}}
 \newcommand\ar{\mathit{ar}}
@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+  In this paper we introduce two extensions of bigraphical reactive systems
+  (BRSs) to handle probabilistic and nondeterministic behaviour, allowing BRSs
+  to be used in discrete-time Markov chain and Markov decision process (MDP)
+  generation. We extend the implementation of an open-source tool for BRSs
+  BigraphER with new syntax for MDP actions and rewards, better visualisation
+  capabilities, and data export options. Furthermore, we introduce a new
+  front-end for working with BRSs based on Jupyter notebooks, allowing the user
+  to quickly visualise bigraphs and reaction rules, simulate execution, or
+  produce a complete transition system, all within the notebook interface.
+  Finally, we demonstrate the modelling capabilities of the new system with a
+  case study on the movement and behaviour of autonomous agents, exploring ideas
+  such as collecting objects, tracking visited locations, hierarchies of spaces,
+  and uncertainty in the topology of space.
 
-\keywords{Bigraphs \and Bigraphical Reactive Systems \and Probabilistic
-  semantics \and Markov decision process.}
+\keywords{Bigraphs \and Bigraphical reactive systems \and Probabilistic
+  semantics \and Discrete-time Markov chain \and Markov decision process \and
+  Spatial models.}
 \end{abstract}
@@
 \section{Introduction}
+
+TODO: DTMC generation, MDP generation: show, define
 
@@
 
-\begin{definition}[rewards]
+\begin{definition}[reward structure]
   A \emph{reward structure} for an MDP $(S, \overline{s}, A, P, L)$ is a pair
@@
 
-% TODO: introduce bigrapher
-From \cite{dblp:journals/tcs/sevegnanic15}.
-From PhD thesis \cite{DBLP:phd/ethos/Sevegnani12}
+% TODO: rework, transition from brs to bigraph
+Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
+universal formalism for modelling interacting systems that evolve in time and
+space. In this paper we use a generalised version of bigraphs, known as
+\emph{bigraphs with sharing}
+\cite{DBLP:phd/ethos/Sevegnani12,dblp:journals/tcs/sevegnanic15}, that uses
+directed acyclic graphs instead of forests to represent node placement, allowing
+one node to be contained in the intersection of several other nodes. In this
+section we introduce the main concepts and definitions in order to expand on
+them in Section~\ref{extensions}.
+
+We begin by introducing some notation used in the definitions. Natural numbers
+are sometimes interpreted as finite ordinals, i.e., $m = \{ 0, \dots, m - 1 \}$.
+We write $S \uplus T$ to indicate the union of sets known or assumed to be
+disjoint. For two functions $f$ and $g$ with disjoint domains $S$ and $T$ we
+write $f \uplus g$ for the function with domain $S \uplus T$ such that $(f
+\uplus g)|_S = f$ and $(f \uplus g)|_T = g$. The identity function on the set
+$S$ is written as $\Id_S$. Given a binary relation $\mathit{rel} \subseteq A
+\times B$, we denote the domain restriction of $\mathit{rel}$ over $S \subseteq
+A$ by $S \lhd \mathit{rel}$. Similarly, we write $\mathit{rel} \rhd S$ for the
+range restriction of $\mathit{rel}$ over $S \subseteq B$. We also denote the
+transitive closure of $\mathit{rel}$ by $\mathit{rel}^+$. In defining bigraphs
+we assume that names, node identifiers, edge identifiers, and controls are drawn
+from four infinite pairwise disjoint sets, respectively $\mathcal{X},
+\mathcal{V}, \mathcal{E}$, and $\mathcal{K}$.
 
@@
 
-Consider the graphical representation of a bigraph in Fig.
-\ref{example_bigraph}. The white ellipses are the \emph{nodes}. Each node has a
-type, called \emph{control}, denoted here by the labels \textsf{A}, \textsf{B},
-and \textsf{C}. The two white dashed rectangles represent \emph{regions},
-i.e. parents of any otherwise parentless nodes. Grey dashed rectangles are
-called \emph{sites} and encode parts of the model that have been abstracted
-away. Nodes, sites, and regions are also known as \emph{places}. Two places with
-the same parent, or two points with the same link are called \emph{siblings}.
+Informally, a bigraph can be thought of as a graph, where a node can be inside
+another node (in this case it can even be in an intersection of several nodes).
+However, the pictures tend to become much clearer if we instead visualise the
+nesting relations between nodes as just a different type of edges. Consider the
+bigraph in Fig.~\ref{example_bigraph}. The white ellipses are the \emph{nodes}.
+Each node has a type, called \emph{control}, and denoted here by the labels
+$\mathsf{A}, \mathsf{B}$, and $\mathsf{C}$. The green edges are actually
+hyperedges (can connect any positive number of nodes), and are called
+\emph{links}. In this example they are given names $\mathsf{x}, \mathsf{y}$, and
+$\mathsf{e}$. Each node has an ordered list of \emph{ports} (not pictured in
+the diagram) that can be thought of as sockets for links. Nodes of the same
+control have the same number of ports. The number of ports a node of control
+$\mathsf{K}$ can have is called the \emph{arity} of $\mathsf{K}$ and is denoted
+by $\ar(\mathsf{K})$. The two white dashed rectangles represent \emph{regions},
+and in this representation are the parents to any otherwise parentless nodes.
+Grey dashed rectangles are called \emph{sites}, and encode parts of the model
+that have been abstracted away. Nodes, sites, and regions are also known as
+\emph{places}. The directed black arrows between places show the containment
+relations, e.g., the $\mathsf{A}$ node has two children (inner nodes):
+$\mathsf{B}$ and the only site in this bigraph, labelled by the number $0$.
+
+Another, more formal way to think about a bigraph is as a pair of graphs: one
+for describing the placement of nodes, and one for the links between them. This
+is the approach that will be featured in our formal definitions. We also focus
+on \emph{concrete} bigraphs, where nodes and links have distinct identifiers.
 
@@
 
+We define several operations on place graphs that will be used later.
+
 \begin{definition}[composition for place graphs with sharing]
@@
   \[ G \circ F = (V, \ctrl, \prnt) : k \to n \]
-  has nodes $V = V_F \uplus V_G$ and control map $\ctrl = \ctrl_F \uplus
-  \ctrl_G$. Its parent relation $\prnt \subseteq (k \uplus V) \times (V \uplus
-  n)$ is given by:
+  has nodes $V \coloneqq V_F \uplus V_G$ and a control map $\ctrl \coloneqq
+  \ctrl_F \uplus \ctrl_G$. Its parent relation $\prnt \subseteq (k \uplus V)
+  \times (V \uplus n)$ is given by:
   \[ \prnt \coloneqq \prnt_G^\lhd \uplus \prnt_\circ \uplus \prnt_F^\rhd, \]
@@
 \begin{definition}[tensor product for place graphs]
-  If $G_0 : m_0 \to n_0$ and $G_1 : m_1 \to n_1$ are two concrete place graphs
-  with sharing with $V_F \cap V_G = \emptyset$, their tensor product
+  If 
+  \[ G_0 = (V_{G_0}, \ctrl_{G_0}, \prnt_{G_0}) : m_0 \to n_0 \]
+  and
+  \[ G_1 = (V_{G_1}, \ctrl_{G_1}, \prnt_{G_1}) : m_1 \to n_1 \]
+  are two concrete place 
+  graphs with sharing with $V_{G_0} \cap V_{G_1} = \emptyset$, their tensor
+  product
   \[ G_0 \otimes G_1 = (V, \ctrl, \prnt) : m_0 + m_1 \to n_0 + n_1 \]
-  has nodes $V = V_{G_0} \uplus V_{G_1}$ and control map $\ctrl \coloneqq
-  \ctrl_{G_0} \uplus \ctrl_{G_1}$. Its parent relation $\prnt \subseteq [(m_0 +
-  m_1) \uplus V] \times [V \uplus (n_0 + n_1)]$ is defined as
+  has nodes $V \coloneqq V_{G_0} \uplus V_{G_1}$ and a control map $\ctrl
+  \coloneqq \ctrl_{G_0} \uplus \ctrl_{G_1}$. Its parent relation $\prnt
+  \subseteq [(m_0 + m_1) \uplus V] \times [V \uplus (n_0 + n_1)]$ is defined as
   \[ \prnt_{G_0} \uplus \prnt_{G_1}^{(m_0, n_0)}, \]
@@
     \prnt_{G_1}^{(m_0, n_0)} = &\{ (v, w) \mid (v, w) \in \prnt_{G_1} \text{ and } v, w \in V_{G_1} \} \\
-    \uplus &\{ (m_0 + i, w) \mid (i, w) \in \prnt_{G_1}, w \in V_{G_1} \text{ and } i \in m_1 \} \\
-    \uplus &\{ (v, n_0 + i) \mid (v, i) \in \prnt_{G_1}, v \in V_{G_1} \text{ and } i \in n_1 \} \\
-    \uplus &\{ (m_0 + i, n_0 + j) \mid (i, j) \in \prnt_{G_1}, i \in m_1, \text{ and } j \in n_1 \}.
+    \uplus &\{ (m_0 + i, w) \mid (i, w) \in \prnt_{G_1}, w \in V_{G_1} \text{, and } i \in m_1 \} \\
+    \uplus &\{ (v, n_0 + i) \mid (v, i) \in \prnt_{G_1}, v \in V_{G_1} \text{, and } i \in n_1 \} \\
+    \uplus &\{ (m_0 + i, n_0 + j) \mid (i, j) \in \prnt_{G_1}, i \in m_1 \text{, and } j \in n_1 \}.
   \end{align*}
@@
   is a quadruple having an inner face $X$ and an outer face $Y$, both finite
-  subsets of $\mathcal{X}$, called respectivelly the inner and outer names of
-  the link graph. $F$ has finite sets $V_F \subset \mathcal{V}$ of nodes and
-  $E_F \subset \mathcal{E}$ of edges, a control map $\ctrl_F : V_F \to
-  \mathcal{K}$ and a \emph{link map}
+  subsets of $\mathcal{X}$, called respectivelly the \emph{inner} and
+  \emph{outer names} of the link graph. $F$ has finite sets $V_F \subset
+  \mathcal{V}$ of nodes and $E_F \subset \mathcal{E}$ of edges, a control map
+  $\ctrl_F : V_F \to \mathcal{K}$ and a \emph{link map}
   \[ \link_F : X \uplus P_F \to E_F \uplus Y, \]
@@
 
-The sets of points and the set of ports of a link $l$ are defined by
-\[ \points_F(l) \coloneqq \{ p \mid \link_F(p) = l \}, \quad \ports_F(l)
-  \coloneqq \points_F(l) \setminus X. \]
-An edge is \emph{idle} if it has no points. Identities over name sets are
-defined by $\id_X = (\emptyset, \emptyset, \emptyset, \Id_X) : X \to X$.
+Two places with the same parent, or two points with the same link are called
+\emph{siblings}. A link is \emph{idle} if it has no points. Identities over
+(inner or outer) name sets are defined by $\id_X = (\emptyset, \emptyset,
+\emptyset, \Id_X) : X \to X$.
 
@@
 
-Given a set of reaction rules, we refer to the configurations that a system may
-adopt as \emph{states}. A bigraph with inner face $\epsilon$ is called
-\emph{ground}.
+We use $\epsilon$ as a shorthand for interface $\langle 0, \emptyset \rangle$. A
+bigraph with inner face $\epsilon$ is called \emph{ground}.
 
@@
 
-Lastly, BigraphER supports \emph{rule priorities}
-\cite{DBLP:journals/tcs/BaetenBKW89}, i.e., a partial ordering on the reaction
+Given a set of reaction rules, we refer to the configurations that a system may
+adopt as \emph{states}. \emph{Rule priorities}
+\cite{DBLP:journals/tcs/BaetenBKW89} impose a partial ordering on the reaction
 rules, where a rule of lower priority can be applied only if no rule of higher
@@
 
-\section{Extensions to Bigraphs}
+\emph{Predicates} can be used to generate labels for states (as in
+Definition~\ref{mdp}) or to ease understanding and debugging of the system. They
+are expressed in a subset of a logic called BiLog
+\cite{DBLP:conf/icalp/ConfortiMS05}, allowing any predicate to be encoded as a
+bigraph \cite{DBLP:journals/scp/CalderKSS14,DBLP:phd/ethos/Sevegnani12}.
+Therefore, we can check each state for any satisfied predicates by solving a
+bigraph matching problem.
+
+\section{Extensions to Bigraphs} \label{extensions}
 
@@
   ground probabilistic reaction rules, where for each $r_i$, there exists a
-  bigraph $D_i$ such that $g = D_ir_i$. Let $S = \{ (r_i, r'_i, p_i) \mid g' =
-  D_ir'_i \}$ (for the same $D_i$), and
+  bigraph $D_i$ such that $g = D_i \circ r_i$. Let $S = \{ (r_i, r'_i, p_i) \mid
+  g' = D_i \circ r'_i \}$ (for the same $D_i$), and
   \[ s = \sum_{i=1}^n p_i. \]
@@
   $a$, where for each $r_i$, there exists a bigraph $D_i$ such that $g =
-  D_ir_i$. Let $S = \{ (r_i, r'_i, a, p_i) \mid g' = D_ir'_i \}$ (for the same
-  $D_i$), and
+  D_i \circ r_i$. Let $S = \{ (r_i, r'_i, a, p_i) \mid g' = D_i \circ r'_i \}$
+  (for the same $D_i$), and
   \[ s = \sum_{i=1}^n p_i. \]
@@
 
-BigraphER \cite{DBLP:conf/cav/SevegnaniC16} supports defining predicates, i.e.,
-bigraphs that are compared to every encountered state. We can associate a reward
-with each predicate, allowing us to assign rewards to states in a flexible and
-semantically meaningful way: the reward of a state is simply the sum of the
-rewards of all matching predicates (and $0$ in case there are none).
+Finally, we can associate a reward with each predicate, allowing us to assign
+rewards to states in a flexible and semantically meaningful way: the reward of a
+state is simply the sum of the rewards of all matching predicates (and $0$ in
+case there are none).
 
 \section{Implementation}
+
+TODO: introduce BigraphER \cite{DBLP:conf/cav/SevegnaniC16}
 
@@
 
-The MDP can be represented as an NBRS with BigraphER code in Listing
-\ref{example_listing}. Furthermore, the BigraphER's visualisation of the
-(automatically generated) transition system is in Fig. \ref{example_ts}.
+The MDP can be represented as an NBRS with BigraphER code in
+Listing~\ref{example_listing}. Furthermore, the BigraphER's visualisation of the
+(automatically generated) transition system is in Fig.~\ref{example_ts}.
 
@@
 transition system or a simulation, labels from predicates, and state/transition
-rewards can be exported to the corresponding PRISM plain text formats.
+rewards can be exported to the various plain text formats of a probabilistic
+model checker PRISM \cite{DBLP:conf/cav/KwiatkowskaNP11} for further
+quantitative analysis.
 
-% TODO: introduce this
+TODO: introduce jupyter (with more/new screenshots)
+
 \begin{figure}
@@
 
-% TODO: Akin to \cite{dblp:conf/nfm/giaquintahimn18} and maybe \cite{koenig1998xavier}.
+TODO: Akin to \cite{dblp:conf/nfm/giaquintahimn18} and maybe
+\cite{koenig1998xavier}.
 
@@
 
-% TODO: what is a link, mention that it's a hyperedge (at least one node)
-% TODO: explain the syntax of the language
+TODO: explain the syntax of the language
+
 Our first scenario is concerned with collecting objects in a grid-like
@@
 
-We begin with a list of controls in Listing \ref{agent1_controls}. On the right
+We begin with a list of controls in Listing~\ref{agent1_controls}. On the right
 hand side of each equal sign is the number of ports that each node of that
@@
 
-Next, we define two predicates: \texttt{home} and \texttt{goal} (see Listing
-\ref{agent1_code}). The former states that the agent is home
-if it is in the southwest corner of the grid,
-while the latter specifies a goal of collecting one object. A larger number of
-objects can be set by nesting \texttt{Object}s inside each other, e.g.,
-\texttt{Agent.Object.Object}. Additionally, Listing \ref{agent1_code} defines
-the initial $2 \times 2$ grid, as described previously.
+Next, we define two predicates: \texttt{home} and \texttt{goal} (see
+Listing~\ref{agent1_code}). The former states that the agent is home if it is in
+the southwest corner of the grid, while the latter specifies a goal of
+collecting one object. A larger number of objects can be set by nesting
+\texttt{Object}s inside each other, e.g., \texttt{Agent.Object.Object}.
+Additionally, Listing~\ref{agent1_code} defines the initial $2 \times 2$ grid,
+as described previously.
 
@@
 cell for the first time, and one for visiting a cell for the first time and
-finding an object. We will use the rules for going north in Listing
-\ref{agent1_north} as an example. When going to an already visited cell, the
-\texttt{Agent} simply traverses a link between the \texttt{North} node of its
-previous \texttt{Cell} and the corresponding \texttt{South} node. As this is the
-only reaction rule for this situation, its probability is $1$. When going to an
-unvisited node, we collect an \texttt{Object} with probability $p$, or make the
-transition without getting an \texttt{Object} with probability $1-p$.
+finding an object. We will use the rules for going north in
+Listing~\ref{agent1_north} as an example. When going to an already visited cell,
+the \texttt{Agent} simply traverses a link between the \texttt{North} node of
+its previous \texttt{Cell} and the corresponding \texttt{South} node. As this is
+the only reaction rule for this situation, its probability is $1$. When going to
+an unvisited node, we collect an \texttt{Object} with probability $p$, or make
+the transition without getting an \texttt{Object} with probability $1-p$.
 Regardless, the \texttt{Cell} changes its link from \texttt{Unvisited} to
@@
 actions for going home have two reaction rules each, depending on whether the
-destination cell is visited or not. They are just like the rules in Listing
-\ref{agent1_north}, except every mention of \texttt{Agent} is replaced with
-\texttt{goal}. The rule to stay home simply says that if the agent has achieved
-the goal, and is home (characterised by a \texttt{Cell} with only two
+destination cell is visited or not. They are just like the rules in
+Listing~\ref{agent1_north}, except every mention of \texttt{Agent} is replaced
+with \texttt{goal}. The rule to stay home simply says that if the agent has
+achieved the goal, and is home (characterised by a \texttt{Cell} with only two
 directions: \texttt{North} and \texttt{East}), then nothing should change (see
-Listing \ref{agent1_home}). To make the agent start heading home as soon as
+Listing~\ref{agent1_home}). To make the agent start heading home as soon as
 enough objects are collected, all five reaction rules related to going and
@@
 
-% TODO: Must mention: \cite{DBLP:conf/giscience/WaltonW12}.
+TODO: Should mention \cite{DBLP:conf/giscience/WaltonW12}.
 
@@
 to link up the \texttt{Node} with one of the \texttt{Cell}s it contains (see
-Fig. \ref{agent2_nesting}). Both \texttt{Cell}s and \texttt{Node}s support
+Fig.~\ref{agent2_nesting}). Both \texttt{Cell}s and \texttt{Node}s support
 having a single link for exactly this purpose. Thus, most of the \texttt{Cell}
 ports are not linked to anything, which is implemented via closures (e.g.
-\texttt{/x Cell\{x\}}). The initial map in Listing \ref{agent2_initial} has a
+\texttt{/x Cell\{x\}}). The initial map in Listing~\ref{agent2_initial} has a
 corridor of three cells, with the agent on the west-most cell, and a door to a
 room in the middle cell. One moves in and out of a room via a pair of actions
-with reaction rules pictured in Fig. \ref{go_in_out}.
+with reaction rules pictured in Fig.~\ref{go_in_out}.
 
@@
 \texttt{Agent} gets to a \texttt{Cell} with an empty \texttt{Node} (represented
-by \texttt{Node\{n\}.1}). In order for this to happen before any other action
-can take place, the two reaction rules in Listing \ref{agent2_room} are put on a
-higher priority class. With probability $p$, the generated room has each
-\texttt{Cell} linked to its two neighbours; and with probability $1-p$, the top
-two \texttt{Cell}s are not linked , possibly forcing the agent to choose a
+by \texttt{Node\{n\}.1})\footnote{Multiple different rooms can be implemented by
+having each previously empty \texttt{Node} contain a node of different control.
+This way a different probability distribution (with different possible outcomes)
+can be assigned to each room.}. In order for this to happen before any other
+action can take place, the two reaction rules in Listing~\ref{agent2_room} are
+put on a higher priority class. With probability $p$, the generated room has
+each \texttt{Cell} linked to its two neighbours; and with probability $1-p$, the
+top two \texttt{Cell}s are not linked, possibly forcing the agent to choose a
 different path. Finally, we have four actions, each with a single reaction rule
@@
 The reaction rules are very similar to those of our previous example, see
-Listing \ref{agent2_north}.
+Listing~\ref{agent2_north}.
 

### 2018-08-10 paper.tex
Sections 1 and 2 are in habitable order (except for the missing intro)

@@
 \keywords{Bigraphs \and Bigraphical reactive systems \and Probabilistic
-  semantics \and Discrete-time Markov chain \and Markov decision process \and
-  Spatial models.}
+  semantics \and Markov decision process \and Spatial models.}
 \end{abstract}
@@
 
-TODO: DTMC generation, MDP generation: show, define
+% TODO: introduction
+%Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
+%universal formalism for modelling interacting systems that evolve in time and
+%space.
+
+%TODO: MDP generation: show, define
 
@@
 \subsection{Bigraphs}
-
-% TODO: rework, transition from brs to bigraph
-Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
-universal formalism for modelling interacting systems that evolve in time and
-space. In this paper we use a generalised version of bigraphs, known as
-\emph{bigraphs with sharing}
-\cite{DBLP:phd/ethos/Sevegnani12,dblp:journals/tcs/sevegnanic15}, that uses
-directed acyclic graphs instead of forests to represent node placement, allowing
-one node to be contained in the intersection of several other nodes. In this
-section we introduce the main concepts and definitions in order to expand on
-them in Section~\ref{extensions}.
 
@@
 Informally, a bigraph can be thought of as a graph, where a node can be inside
-another node (in this case it can even be in an intersection of several nodes).
-However, the pictures tend to become much clearer if we instead visualise the
-nesting relations between nodes as just a different type of edges. Consider the
-bigraph in Fig.~\ref{example_bigraph}. The white ellipses are the \emph{nodes}.
-Each node has a type, called \emph{control}, and denoted here by the labels
+another node\footnote{To be specific, in this paper we extend the ideas behind
+  \emph{bigraphs with sharing}
+  \cite{DBLP:phd/ethos/Sevegnani12,dblp:journals/tcs/sevegnanic15}, where a node
+  can be contained in the intersection of several other nodes.}. However, the
+pictures tend to become much clearer if we instead visualise the nesting
+relations between nodes as just a different type of edges. Consider the bigraph
+in Fig.~\ref{example_bigraph}. The white ellipses are the \emph{nodes}. Each
+node has a type, called \emph{control}, and denoted here by the labels
 $\mathsf{A}, \mathsf{B}$, and $\mathsf{C}$. The green edges are actually
@@
 \emph{links}. In this example they are given names $\mathsf{x}, \mathsf{y}$, and
-$\mathsf{e}$. Each node has an ordered list of \emph{ports} (not pictured in
-the diagram) that can be thought of as sockets for links. Nodes of the same
-control have the same number of ports. The number of ports a node of control
+$\mathsf{e}$. Each node has an ordered list of \emph{ports} (not pictured in the
+diagram) that can be thought of as sockets for links. Nodes of the same control
+have the same number of ports. The number of ports a node of control
 $\mathsf{K}$ can have is called the \emph{arity} of $\mathsf{K}$ and is denoted
@@
 
-\section{Extensions to Bigraphs} \label{extensions}
+\section{Extensions to BRSs} \label{extensions}
 
-\subsection{Probabilistic Bigraphs}
+We propose two new BRSs: one adds probabilities to reaction rules, the other
+also groups the rules into actions and supports rewards based on both reaction
+rules and predicates. The main technicality in both the definitions and the
+implementation is that after generating a list of applicable ground reaction
+rules (for a particular action, if appropriate), the probabilities need to be
+normalised so that they add to $1$, as a single reaction rule can sometimes be
+applied in multiple places, or some rules in an action may not be applicable.
+
+\subsection{Probabilistic BRS}
 
@@
 
-\subsection{Nondeterministic Bigraphs}
+\subsection{Nondeterministic BRS}
 

### 2018-08-11 paper.tex
Describing Jupyter

@@
 \usepackage{siunitx}
+\usepackage{hyperref}
 % If you use the hyperref package, please uncomment the following line
 % to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+ \renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
   is a quadruple having an inner face $X$ and an outer face $Y$, both finite
-  subsets of $\mathcal{X}$, called respectivelly the \emph{inner} and
+  subsets of $\mathcal{X}$, called respectively the \emph{inner} and
   \emph{outer names} of the link graph. $F$ has finite sets $V_F \subset
@@
   reaction rule, and $a \in A$ is an action. We also define a \emph{reaction
-    reward function} $r : A \to \mathbb{R}$ that assigns a reward/cost to each
-  action.
+    reward function} $r : A \to \mathbb{R}$ that assigns a reward or cost to
+  each action.
 \end{definition}
@@
 
-TODO: introduce BigraphER \cite{DBLP:conf/cav/SevegnaniC16}
+% TODO: introduce BigraphER \cite{DBLP:conf/cav/SevegnaniC16} and its syntax
 
@@
 The MDP can be represented as an NBRS with BigraphER code in
-Listing~\ref{example_listing}. Furthermore, the BigraphER's visualisation of the
-(automatically generated) transition system is in Fig.~\ref{example_ts}.
+Listing~\ref{example_listing}. BigraphER can construct and visualise the full
+transition system, as in Fig.~\ref{example_ts}.
 
@@
 highlighted with a thicker border), and each action (per state) is a grey
-ellipse. Text inside state ellipses lists all predicates that are satisfied by
-that state. Edges from actions to states are labelled with both the probability
-and the name of the reaction rule. Transitions from either a fully generated
-transition system or a simulation, labels from predicates, and state/transition
-rewards can be exported to the various plain text formats of a probabilistic
-model checker PRISM \cite{DBLP:conf/cav/KwiatkowskaNP11} for further
-quantitative analysis.
+ellipse. The labels inside state ellipses list all predicates that are
+satisfied by that state. Edges from actions to states are labelled with both the
+probability and the name of the reaction rule. Transitions from either a fully
+generated transition system or a simulation, labels from predicates, and
+state/transition rewards can be exported to the various plain text formats of a
+probabilistic model checker PRISM \cite{DBLP:conf/cav/KwiatkowskaNP11} for
+further quantitative analysis.
 
-TODO: introduce jupyter (with more/new screenshots)
+\subsection{Front end}
 
@@
   \centering
-  \includegraphics{images/interface.jpg}
-  \caption{The BigraphER Jupyter interface with syntax highlighting.}
+  \includegraphics[width=\textwidth]{images/jupyter.jpg}
+  \caption{The BigraphER Jupyter notebook interface with syntax highlighting.}
   \label{interface}
 \end{figure}
+
+We introduce a new front end to BigraphER based on Jupyter notebooks
+\cite{DBLP:conf/elpub/KluyverRPGBFKHG16}. The BigraphER kernel is an extension
+to the OCaml kernel\footnote{\url{https://github.com/akabe/ocaml-jupyter}} and
+is available on
+GitHub\footnote{\url{https://github.com/dilkas/bigrapher-jupyter}}. It supports
+a similar workflow to that of Jupyter notebooks for other languages, allowing
+the user to divide the code into multiple \emph{cells} and have the definitions
+persist in a \emph{buffer} to be used later. By default, the output of each cell
+displays the graphical representation of all bigraphs and reaction rules defined
+in that cell (see Fig. \ref{interface} for an example). The generated images are
+stored in a local directory \texttt{jupyter-images/}. The kernel also supports a
+number of \emph{magics}, i.e., custom commands that can be used at the top of a
+cell:
+
+\begin{description}
+  \item[\texttt{\%states}] produces a state transition diagram (similar to the
+    one in Fig. \ref{example_ts}). Mousing over a state shows what that
+    state looks like as a bigraph.
+  \item[\texttt{\%simulate n}] runs a simulation for \texttt{n} steps, when used
+    on non-stochastic models. For stochastic BRSs
+    \cite{DBLP:journals/entcs/KrivineMT08}, \texttt{n} is interpreted as a
+    floating-point number, representing maximum simulation time. The produced
+    diagram is a single path through the transition system with the same
+    mouse-over functionality.
+  \item[\texttt{\%output}] displays the full output produced by BigraphER. By
+    default, only errors are displayed in the notebook.
+  \item[\texttt{\%ocaml}] allows full backward compatibility with the OCaml
+    kernel, including auto-complete and integrated documentation features that
+    have been extended to the BigraphER OCaml API as well as plotting support
+    with Archimedes\footnote{\url{http://archimedes.forge.ocamlcore.org/}}.
+  \item[\texttt{\%clear}] clears the buffer before interpreting the code from
+    the current cell.
+\end{description}
 
@@
 \subsection{Collecting Objects in a Grid}
-
-TODO: explain the syntax of the language
 
@@
 
-In order to impement nesting, a \texttt{Cell} contains a \texttt{Node}, which
+In order to implement nesting, a \texttt{Cell} contains a \texttt{Node}, which
 can have any number of \texttt{Cell}s of its own. Since after entering a room,

### 2018-08-11 paper.tex
Section 3 is (kind of) done

@@
 
-% TODO: introduce BigraphER \cite{DBLP:conf/cav/SevegnaniC16} and its syntax
+The described extensions have been implemented in an open-source tool for BRSs
+BigraphER \cite{DBLP:conf/cav/SevegnaniC16}. We refer the interested reader to
+the paper on BigraphER \cite{DBLP:conf/cav/SevegnaniC16}, the related PhD thesis
+\cite{DBLP:phd/ethos/Sevegnani12}, and online
+resources\footnote{\url{http://www.dcs.gla.ac.uk/~michele/bigrapher.html}} for
+further information on the syntax and capabilities of the software. In this
+section we will introduce the new features of BigraphER by using a simple MDP as
+an example.
 
@@
   Consider an MDP $(S, \overline{s}, A, P, L)$, where $S = \{ s_0, s_1, s_2, s_3
-  \}$, $\overline{s} = s_0$, $A = \{ a, b, c \}$, and $P, L$ defined as follows:
+  \}$, $\overline{s} = s_0$, $A = \{ a, b, c \}$, and $P, L$ are defined as
+  follows:
   \begin{equation*}
@@
 The MDP can be represented as an NBRS with BigraphER code in
-Listing~\ref{example_listing}. BigraphER can construct and visualise the full
-transition system, as in Fig.~\ref{example_ts}.
+Listing~\ref{example_listing}. More specifically, reaction rule probabilities
+are represented as floating-point numbers inside the arrows (e.g.
+\texttt{-[0.7]->}), each action encompasses its reaction rules with
+\texttt{\textbf{action} actionName} and \texttt{\textbf{end}}. Rewards can be
+added to actions simply by inserting an integer enclosed in squared brackets
+after the action name (e.g. \texttt{\textbf{action} b[1]}). Lastly, predicate
+rewards have the same format, but are listed on the \texttt{\textbf{preds}} line
+of the \texttt{\textbf{begin nbrs}}---\texttt{\textbf{end}} block (e.g.
+\texttt{\textbf{preds} = \{heads[3]\};}).
 
-More specifically, reaction rule probabilities are represented as floating-point
-numbers inside the arrows (e.g. \texttt{-[0.7]->}), each action encompasses its
-reaction rules with \texttt{\textbf{action} actionName} and
-\texttt{\textbf{end}}. Rewards can be added to actions simply by inserting an
-integer enclosed in squared brackets after the action name (e.g.
-\texttt{\textbf{action} b[1]}). Lastly, predicate rewards have the same format,
-but are listed on the \texttt{\textbf{preds}} line of the \texttt{\textbf{begin
-    nbrs}}---\texttt{\textbf{end}} block (e.g. \texttt{\textbf{preds} =
-  \{heads[3]\};}).
-
-Visually, each state is represented by a white ellipse (the starting state is
-highlighted with a thicker border), and each action (per state) is a grey
-ellipse. The labels inside state ellipses list all predicates that are
-satisfied by that state. Edges from actions to states are labelled with both the
-probability and the name of the reaction rule. Transitions from either a fully
-generated transition system or a simulation, labels from predicates, and
+BigraphER can construct and visualise the full transition system (see
+Fig.~\ref{example_ts}). Each state is represented by a white ellipse (the
+starting state is highlighted with a thicker border), and each action (per
+state) is a grey ellipse. The labels inside state ellipses list all predicates
+that are satisfied by that state. Edges from actions to states are labelled with
+both the probability and the name of the reaction rule. Transitions from either
+a fully generated transition system or a simulation, labels from predicates, and
 state/transition rewards can be exported to the various plain text formats of a

### 2018-08-12 paper.tex
Adding some citations

@@
 %space.
-
-%TODO: MDP generation: show, define
 
@@
   where $P_F \coloneqq \{ (v, i) \mid i \in \ar(\ctrl_F(v)) \}$ is the set of
-  ports of $F$. Thus $(v, i)$ is the $i$th port of node $v$. We shall call $X
+  ports of $F$. Thus, $(v, i)$ is the $i$th port of node $v$. We shall call $X
   \uplus P_F$ the \emph{points} of $F$, and $E_F \uplus Y$ its \emph{links}.
@@
 
-TODO: Akin to \cite{dblp:conf/nfm/giaquintahimn18} and maybe
-\cite{koenig1998xavier}.
+In order to demonstrate the use of bigraphs in modelling probabilistic
+processes with nondeterminism, we present two examples of agent movement
+planning in two dimensions. The examples have different sources of probabilistic
+behaviour and explore topics such as tracking visited locations and uncertainty
+about the topology.
+
+% TODO advantages: more visual/realistic than a vector of numbers, rewards and
+% transition rules can be generated with a higher degree of automation, less
+% code, more flexible (changing size of the grid); disadvantages: constant
+% probability (without hacking)
+
+% TODO xavier \cite{koenig1998xavier}
 
@@
 Our first scenario is concerned with collecting objects in a grid-like
-two-dimensional world. The agent starts in the southwest corner of the map
-(which we call \emph{home}), explores the environment until it collects a
-specified number of objects, and returns home (while possibly collecting more
-objects along the way). The model tracks which cells of the grid have been
-explored, and only the unexplored cells have a constant probability $p$ of
-rewarding the agent with an object. The desired number of objects can be easily
-changed, and the map can be customised to make some transitions unavailable
-(i.e. add walls), as long as the agent can still return home.
+two-dimensional world and is inspired by similar scenarios modelled using PRISM
+\cite{dblp:conf/nfm/giaquintahimn18,DBLP:conf/spin/HoffmannIMNV16}. The agent
+starts in the southwest corner of the map (which we call \emph{home}), explores
+the environment until it collects a specified number of objects, and returns
+home (while possibly collecting more objects along the way). The model tracks
+which cells of the grid have been explored, and only the unexplored cells have a
+constant probability $p$ of rewarding the agent with an object. The desired
+number of objects can be easily changed, and the map can be customised to make
+some transitions unavailable (i.e. add walls), as long as the agent can still
+return home.
 
@@
 
-TODO: Should mention \cite{DBLP:conf/giscience/WaltonW12}.
-
 Our second model explores two important concepts in modelling the topology of
@@
 versa (e.g., using a door to enter or leave a room). In the rest of the paper,
-whenever we discuss one space inside another, we will refer to the inner space
-as the \emph{room}.
+whenever we discuss one space nested inside another, we will refer to the inner
+space as the \emph{room}. While nesting has been modelled using bigraphs before
+\cite{DBLP:conf/giscience/WaltonW12}, our approach models each room not as a
+single entity, but rather as an interconnected collection of smaller spaces,
+which we continue to call \emph{cells}. Thus, it is not enough to be in the
+hallway in order to enter a room, one needs to be next to the door. Similarly,
+after entering a room, the agent is positioned next to the other side of the
+door.
 
@@
 As the ideas of collecting objects and tracking visited cells have been
-explored already, they are dropped from this model to simplify the
+explored already, they are dropped from this model in order to simplify the
 implementation. The goal can simply be defined as moving from one location to
@@
 
-In order to implement nesting, a \texttt{Cell} contains a \texttt{Node}, which
-can have any number of \texttt{Cell}s of its own. Since after entering a room,
-you end up in a specific place inside the room (next to the door), we also need
-to link up the \texttt{Node} with one of the \texttt{Cell}s it contains (see
-Fig.~\ref{agent2_nesting}). Both \texttt{Cell}s and \texttt{Node}s support
-having a single link for exactly this purpose. Thus, most of the \texttt{Cell}
-ports are not linked to anything, which is implemented via closures (e.g.
-\texttt{/x Cell\{x\}}). The initial map in Listing~\ref{agent2_initial} has a
-corridor of three cells, with the agent on the west-most cell, and a door to a
-room in the middle cell. One moves in and out of a room via a pair of actions
-with reaction rules pictured in Fig.~\ref{go_in_out}.
+In order to implement nesting, we put a \texttt{Node} (representing a room)
+inside a \texttt{Cell}, which has the ``door'' to that room (see Fig.
+\ref{agent2_nesting}). The \texttt{Node} can have its own collection of
+\texttt{Cell}s, describing the topology of the room. One of these \texttt{Cell}s
+is linked to the \texttt{Node}, representing the \texttt{Cell} closest to the
+door from the inside of the room. Thus, both \texttt{Node}s and \texttt{Cell}s
+have arity $1$ for exactly this linking. \texttt{Cell} ports not linked to
+anything are implemented using closures (e.g. \texttt{/x Cell\{x\}}). The
+initial map in Listing~\ref{agent2_initial} has a corridor of three cells with
+the agent on the west-most cell and a door to a room in the middle cell. One
+moves in and out of a room using a pair of actions with reaction rules pictured
+in Fig.~\ref{go_in_out}.
 
@@
 This way a different probability distribution (with different possible outcomes)
-can be assigned to each room.}. In order for this to happen before any other
-action can take place, the two reaction rules in Listing~\ref{agent2_room} are
-put on a higher priority class. With probability $p$, the generated room has
+can be assigned to each room.}. In order for the room to be generated before any
+other action can take place, the two reaction rules in Listing~\ref{agent2_room}
+are put on a higher priority class. With probability $p$, the generated room has
 each \texttt{Cell} linked to its two neighbours; and with probability $1-p$, the
@@
 with probability $1$, corresponding to the four possible directions of travel.
-The reaction rules are very similar to those of our previous example, see
-Listing~\ref{agent2_north}.
+The reaction rules are very similar to those of our previous example, an example
+of which can be found in Listing~\ref{agent2_north}.
 
 \section{Conclusion}
+
+BIG TODO!
 

### 2018-08-12 paper.tex
TikZ illustrations to the rescue!

@@
 \usepackage{hyperref}
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
+\usepackage{tikz}
+\usepackage{phaistos}
+
 \renewcommand\UrlFont{\color{blue}\rmfamily}
@@
 \begin{document}
+
 \title{Nondeterministic Bigraphical Reactive Systems for Markov Decision
@@
 
-% TODO advantages: more visual/realistic than a vector of numbers, rewards and
-% transition rules can be generated with a higher degree of automation, less
-% code, more flexible (changing size of the grid); disadvantages: constant
-% probability (without hacking)
-
 % TODO xavier \cite{koenig1998xavier}
@@
 
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    % walls
+    \draw (3, 2) -- (3, 0) -- (1, 0) -- (1, 2) -- (0, 2) -- (0, 3) -- (3, 3) -- (3, 2) -- (2, 2);
+    \draw[brown,ultra thick] (1, 2) -- (2, 2);
+    % the door
+    \draw[red,ultra thick,dashed] (2, 2) -- (2, 1);
+    % the background grid
+    \draw[gray,very thin] (1, 3) -- (1, 2);
+    \draw[gray,very thin] (2, 3) -- (2, 2);
+    \draw[gray,very thin] (1, 1) -- (3, 1);
+    \draw[gray,very thin] (2, 1) -- (2, 0);
+    % the agent
+    \node at (0.5, 2.3) {\PHchild};
+  \end{tikzpicture}
+  \caption{The full map. The agent is in the top left cell. There is a thick
+    brown door connecting the middle cell of the top row with a $2 \times 2$
+    room below. The red dashed wall exists with probability $1-p$.}
+  \label{agent2_map}
+\end{figure}
+
 \lstinputlisting[caption={Two ways to generate a room, leaving one door either
@@
 top two \texttt{Cell}s are not linked, possibly forcing the agent to choose a
-different path. Finally, we have four actions, each with a single reaction rule
-with probability $1$, corresponding to the four possible directions of travel.
-The reaction rules are very similar to those of our previous example, an example
-of which can be found in Listing~\ref{agent2_north}.
+different path (see Fig. \ref{agent2_map}). Finally, we have four actions, each
+with a single reaction rule with probability $1$, corresponding to the four
+possible directions of travel. The reaction rules are very similar to those of
+our previous example, an example of which can be found in
+Listing~\ref{agent2_north}.
 
@@
 
-BIG TODO!
+% TODO advantages: more visual/realistic than a vector of numbers, rewards and
+% transition rules can be generated with a higher degree of automation, less
+% code, more flexible (changing size of the grid); disadvantages: constant
+% probability (without hacking)
 

### 2018-08-13 paper.tex
TODOs + MDP references + a prettier door

@@
 
+% TODO: opening statement on why probabilities and non-determinism are important
 \begin{abstract}
@@
 
+% TODO: short intro on MDPs with references to the literature, why they are
+% important
+% TODO: turn the door into an actual door
+
+MDPs have been used to solve a wide range of problems: optimising airline yield
+management \cite{DBLP:journals/transci/LautenbacherS99}, constructing optimal
+dialogue strategies \cite{658989,DBLP:conf/icassp/LevinPE98}, electricity supply
+bidding \cite{867150}, and many others.
+
+% TODO xavier \cite{koenig1998xavier}
 \begin{definition}[Markov decision process] \label{mdp}
@@
 \end{definition}
+
+% TODO: minimal example with a diagram
 
@@
 
+% TODO: site should be at the bottom
 \begin{figure}
@@
 
+% TODO: mention we will be using bigraphs with sharing and we recall some
+% definitions from TCS paper
 \begin{definition}[concrete place graph with sharing]
@@
 
+% TODO: why we limit reaction rules to solid (stochastic bigraphs paper)
 \begin{definition}[reaction rule] \label{reaction_rule}
@@
 
+% TODO: for the same D_i - not clear
+% TODO: minimal example showing normalisation
 \begin{definition}[probabilistic reaction rule]
@@
 
+% TODO: intro explaining how we are further generalising the extensions defined
+% above
+
 \begin{definition}[nondeterministic reaction rule]
@@
 
+% TODO: D_i not clear
+% TODO: different symbol for reward
 \begin{definition}[nondeterministic bigraphical reactive system (NBRS)]
@@
 
+% TODO: minimal example, possible the same one as below
+
 \section{Implementation}
+
+% TODO: we extend BigraphER
+% TODO: describe the new syntactical constructs using the example
+% TODO: what's the reward of action b?
 
@@
 
-% TODO xavier \cite{koenig1998xavier}
+% TODO: the agent is simply modelled as an atomic node as the focus of this case
+% study is on its movements across a grid. More complex models are possible
+% by...
 
@@
 
+% TODO: taking advantage of the hierarchical structure of bigraphs
+
 Our second model explores two important concepts in modelling the topology of
@@
   \begin{tikzpicture}
-    % walls
+    % outside walls
     \draw (3, 2) -- (3, 0) -- (1, 0) -- (1, 2) -- (0, 2) -- (0, 3) -- (3, 3) -- (3, 2) -- (2, 2);
-    \draw[brown,ultra thick] (1, 2) -- (2, 2);
-    % the door
+    % the probabilistic wall
     \draw[red,ultra thick,dashed] (2, 2) -- (2, 1);
@@
     \node at (0.5, 2.3) {\PHchild};
+    % the door
+    \draw[dotted] (1.25,2) arc (180:270:0.5cm);
+    \draw[brown,ultra thick] (1.75,1.5) -- (1.75,2) node[right,  near start]{};
+    \draw (1, 2) -- (1.25, 2);
+    \draw (1.75, 2) -- (2, 2);
   \end{tikzpicture}
@@
 
+% TODO: limitation of a single entrance/exit per cell, can a room have multiple
+% doors (doesn't make sense for this conceptualisation of the problem)?
+
+% TODO: state diagrams (and statistics about them)
+% TODO: numerical analysis (or ideas)
+% TODO: discussion section
+% TODO: what are the adtantages of using NBRS?
+% TODO: limitations
+% TODO: difficulties
+
 \section{Conclusion}
@@
 % probability (without hacking)
+% Extensions: multiple agents (nice), uncertainty in actions (easy), rotations
+% (pomdp paper, easy), not limited to four directions
 

### 2018-08-13 paper.tex
Another example of an MDP

@@
 \usepackage{phaistos}
+
+\usetikzlibrary{shapes,arrows.meta}
 
@@
 
-% TODO: short intro on MDPs with references to the literature, why they are
-% important
-% TODO: turn the door into an actual door
-
-MDPs have been used to solve a wide range of problems: optimising airline yield
-management \cite{DBLP:journals/transci/LautenbacherS99}, constructing optimal
-dialogue strategies \cite{658989,DBLP:conf/icassp/LevinPE98}, electricity supply
-bidding \cite{867150}, and many others.
+Markov decision processes \cite{bellman1957markovian,howard1960dynamic} provide
+a way to model decision making in situations with both probabilistic outcomes
+and nondeterministic decision making. They have been used to solve a wide range
+of problems: optimising airline yield management
+\cite{DBLP:journals/transci/LautenbacherS99}, constructing optimal dialogue
+strategies \cite{658989,DBLP:conf/icassp/LevinPE98}, electricity supply bidding
+\cite{867150}, and many others
+\cite{DBLP:journals/questa/StidhamW93,white1985real,white1988further,white1993survey}.
+Furthermore, MDPs have been extended in multiple ways, each extension bringing
+its own applications: constrained MDPs \cite{altman1999constrained}, partially
+observable MDPs \cite{astrom1965optimal}, fuzzy MDPs \cite{fakoor2016humanoid},
+and continuous-time MDPs \cite{guo2009continuous}.
 
@@
 
-% TODO: minimal example with a diagram
+\begin{example}
+  Let $M = (S, \overline{s}, A, P, L)$ be an MDP, where $S = \{ s_0, s_1, s_2,
+  s_3 \}$, $\overline{s} = s_0$, $A = \{ \text{start}, \text{wait}, \text{send},
+  \text{restart}, \text{stop} \}$, and $P, L$ are defined as follows:
+  \begin{equation*}
+    \begin{split}
+      P(s_0, \text{start}) &= P(s_1, \text{wait}) = [s_1 \mapsto 1], \\
+      P(s_1, \text{send}) &= [s_2 \mapsto 0.01, s_3 \mapsto 0.99], \\
+      P(s_2, \text{restart}) &= [s_0 \mapsto 1], \\
+      P(s_3, \text{stop}) &= [s_3 \mapsto 1],
+    \end{split}
+    \qquad
+    \begin{split}
+      L(s_0) &= \emptyset, \\
+      L(s_1) &= \{ \text{try} \}, \\
+      L(s_2) &= \{ \text{failure} \}, \\
+      L(s_3) &= \{ \text{success} \}.
+    \end{split}
+  \end{equation*}
+  Then $M$ can represent a simple communication protocol. The process
+  initialises, and is faced with a nondeterministic choice between waiting and
+  sending a message. Most of the time the sent message is successfully
+  delivered, and the process stops. But sometimes a message fails to deliver, in
+  which case the process has to restart. See Fig. \ref{first_mdp} for a
+  visualisation of $M$.
+\end{example}
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}[state/.style={rectangle, draw, scale=2},
+    action/.style={diamond, draw, fill=lightgray, minimum size=1.6cm}]
+    \node(origin) at (-1, 0){};
+    \node[state](s0) at (0, 0){$s_0$};
+    \node[action](start) at (2, 0){start};
+    \node[state,label=try](s1) at (4, 0){$s_1$};
+    \node[action](wait) at (4, -2){wait};
+    \node[action](send) at (6, 0){send};
+    \node[state,label={right:failure}](s2) at (8, 2){$s_2$};
+    \node[action](restart) at (8, 4){restart};
+    \node[state,label={below:success}](s3) at (8, -2){$s_3$};
+    \node[action](stop) at (10, -2){stop};
+    \draw[-{>[scale=2]}] (s0) edge (start);
+    \draw[-{>[scale=2]}] (start) edge node[above] {$1$} (s1);
+    \draw[-{>[scale=2]},bend left] (s1) edge (wait);
+    \draw[-{>[scale=2]},bend left] (wait) edge node[left] {$1$} (s1);
+    \draw[-{>[scale=2]}] (s1) edge (send);
+    \draw[-{>[scale=2]}] (send) edge node[left] {$0.01$} (s2);
+    \draw[-{>[scale=2]}] (send) edge node[left] {$0.99$} (s3);
+    \draw[-{>[scale=2]}] (s2) edge (restart);
+    \draw[-{>[scale=2]},bend right] (restart) edge node[above] {$1$} (s0);
+    \draw[-{>[scale=2]},bend left] (s3) edge (stop);
+    \draw[-{>[scale=2]},bend left] (stop) edge node[below] {$1$} (s3);
+    \draw[-{>[scale=2]}] (origin) edge (s0);
+  \end{tikzpicture}
+  \caption{A simple MDP for communication.}
+  \label{first_mdp}
+\end{figure}
 
@@
     \begin{split}
-      L(s_0) &= \{ initial \}, \\
+      L(s_0) &= \{ \text{initial} \}, \\
       L(s_1) &= \emptyset, \\
-      L(s_2) &= \{ heads \}, \\
-      L(s_3) &= \{ tails \}.
+      L(s_2) &= \{ \text{heads} \}, \\
+      L(s_3) &= \{ \text{tails} \}.
     \end{split}
@@
   \end{tikzpicture}
-  \caption{The full map. The agent is in the top left cell. There is a thick
-    brown door connecting the middle cell of the top row with a $2 \times 2$
-    room below. The red dashed wall exists with probability $1-p$.}
+  \caption{The full map. The agent is in the top left cell. There is a door
+    connecting the middle cell of the top row with a $2 \times 2$ room below.
+    The dashed wall exists with probability $1-p$.}
   \label{agent2_map}

### 2018-08-15 paper.tex
An OK-ish draft

@@
 
-% TODO: opening statement on why probabilities and non-determinism are important
 \begin{abstract}
-  In this paper we introduce two extensions of bigraphical reactive systems
-  (BRSs) to handle probabilistic and nondeterministic behaviour, allowing BRSs
-  to be used in discrete-time Markov chain and Markov decision process (MDP)
-  generation. We extend the implementation of an open-source tool for BRSs
-  BigraphER with new syntax for MDP actions and rewards, better visualisation
-  capabilities, and data export options. Furthermore, we introduce a new
-  front-end for working with BRSs based on Jupyter notebooks, allowing the user
-  to quickly visualise bigraphs and reaction rules, simulate execution, or
-  produce a complete transition system, all within the notebook interface.
-  Finally, we demonstrate the modelling capabilities of the new system with a
-  case study on the movement and behaviour of autonomous agents, exploring ideas
-  such as collecting objects, tracking visited locations, hierarchies of spaces,
-  and uncertainty in the topology of space.
+  Probabilities and nondeterminism allow us to represent uncertainty and
+  decision making. In this paper we introduce two extensions of bigraphical
+  reactive systems (BRSs) to handle probabilistic and nondeterministic
+  behaviour, allowing BRSs to be used in discrete-time Markov chain and Markov
+  decision process (MDP) generation. We extend the implementation of an
+  open-source tool for BRSs BigraphER with new syntax for MDP actions and
+  rewards, better visualisation capabilities, and data exporting options.
+  Furthermore, we introduce a new front end for working with BRSs based on
+  Jupyter notebooks, allowing the user to quickly visualise bigraphs and
+  reaction rules, simulate execution, or produce a complete transition
+  system---all within the notebook interface. Finally, we demonstrate the
+  modelling capabilities of the new system with a case study on the movement and
+  behaviour of autonomous agents, exploring ideas such as collecting objects,
+  tracking visited locations, hierarchies of spaces, and uncertainty in the
+  topology of space.
 
@@
 
-% TODO: introduction
+TODO: introduction to bigraphs and everything else
 %Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
@@
 
-% TODO xavier \cite{koenig1998xavier}
 \begin{definition}[Markov decision process] \label{mdp}
   For any finite set $X$, let $\Dist(X)$ denote the set of discrete probability
-  distributions over $X$. A \emph{Markov Decision Process} is a tuple $ (S,
+  distributions over $X$. A \emph{Markov Decision Process} is a tuple $(S,
   \overline{s}, A, P, L)$, where: $S$ is a finite set of states and
@@
 
-We begin by introducing some notation used in the definitions. Natural numbers
-are sometimes interpreted as finite ordinals, i.e., $m = \{ 0, \dots, m - 1 \}$.
-We write $S \uplus T$ to indicate the union of sets known or assumed to be
-disjoint. For two functions $f$ and $g$ with disjoint domains $S$ and $T$ we
-write $f \uplus g$ for the function with domain $S \uplus T$ such that $(f
-\uplus g)|_S = f$ and $(f \uplus g)|_T = g$. The identity function on the set
-$S$ is written as $\Id_S$. Given a binary relation $\mathit{rel} \subseteq A
-\times B$, we denote the domain restriction of $\mathit{rel}$ over $S \subseteq
-A$ by $S \lhd \mathit{rel}$. Similarly, we write $\mathit{rel} \rhd S$ for the
-range restriction of $\mathit{rel}$ over $S \subseteq B$. We also denote the
+In this paper we use \emph{bigraphs with sharing} and recall some of the
+definitions from the literature
+\cite{DBLP:phd/ethos/Sevegnani12,dblp:journals/tcs/sevegnanic15}. We begin by
+introducing the notation used in the definitions. Natural numbers are sometimes
+interpreted as finite ordinals, i.e., $m = \{ 0, \dots, m - 1 \}$. We write $S
+\uplus T$ to indicate the union of sets known or assumed to be disjoint. For two
+functions $f$ and $g$ with disjoint domains $S$ and $T$ we write $f \uplus g$
+for the function with domain $S \uplus T$ such that $(f \uplus g)|_S = f$ and
+$(f \uplus g)|_T = g$. The identity function on the set $S$ is written as
+$\Id_S$. Given a binary relation $\mathit{rel} \subseteq A \times B$, we denote
+the domain restriction of $\mathit{rel}$ over $S \subseteq A$ by $S \lhd
+\mathit{rel}$. Similarly, we write $\mathit{rel} \rhd S$ for the range
+restriction of $\mathit{rel}$ over $S \subseteq B$. We also denote the
 transitive closure of $\mathit{rel}$ by $\mathit{rel}^+$. In defining bigraphs
@@
 Informally, a bigraph can be thought of as a graph, where a node can be inside
-another node\footnote{To be specific, in this paper we extend the ideas behind
-  \emph{bigraphs with sharing}
-  \cite{DBLP:phd/ethos/Sevegnani12,dblp:journals/tcs/sevegnanic15}, where a node
-  can be contained in the intersection of several other nodes.}. However, the
-pictures tend to become much clearer if we instead visualise the nesting
-relations between nodes as just a different type of edges. Consider the bigraph
-in Fig.~\ref{example_bigraph}. The white ellipses are the \emph{nodes}. Each
-node has a type, called \emph{control}, and denoted here by the labels
-$\mathsf{A}, \mathsf{B}$, and $\mathsf{C}$. The green edges are actually
-hyperedges (can connect any positive number of nodes), and are called
-\emph{links}. In this example they are given names $\mathsf{x}, \mathsf{y}$, and
-$\mathsf{e}$. Each node has an ordered list of \emph{ports} (not pictured in the
-diagram) that can be thought of as sockets for links. Nodes of the same control
-have the same number of ports. The number of ports a node of control
-$\mathsf{K}$ can have is called the \emph{arity} of $\mathsf{K}$ and is denoted
-by $\ar(\mathsf{K})$. The two white dashed rectangles represent \emph{regions},
-and in this representation are the parents to any otherwise parentless nodes.
-Grey dashed rectangles are called \emph{sites}, and encode parts of the model
-that have been abstracted away. Nodes, sites, and regions are also known as
-\emph{places}. The directed black arrows between places show the containment
-relations, e.g., the $\mathsf{A}$ node has two children (inner nodes):
-$\mathsf{B}$ and the only site in this bigraph, labelled by the number $0$.
+another node (or in the intersection of several nodes). However, the diagrams
+tend to become much clearer if we instead visualise the nesting relations
+between nodes as just a different type of edges. Consider the bigraph in
+Fig.~\ref{example_bigraph}. The white ellipses are the \emph{nodes}. Each node
+has a type, called \emph{control} and denoted here by the labels $\mathsf{A},
+\mathsf{B}$, and $\mathsf{C}$. The green edges are actually hyperedges (can
+connect any positive number of nodes) and are called \emph{links}. In this
+example they are given names $\mathsf{x}, \mathsf{y}$, and $\mathsf{e}$. Each
+node has an ordered list of \emph{ports} (not pictured in the diagram) that can
+be thought of as sockets for links. Nodes of the same control have the same
+number of ports. The number of ports a node of control $\mathsf{K}$ can have is
+called the \emph{arity} of $\mathsf{K}$ and is denoted by $\ar(\mathsf{K})$. The
+two white dashed rectangles represent \emph{regions} and in this representation
+are the parents to any otherwise parentless nodes. Grey dashed rectangles are
+called \emph{sites} and encode parts of the model that have been abstracted
+away. Nodes, sites, and regions are also known as \emph{places}. The directed
+black arrows between places show the containment relations, e.g., the
+$\mathsf{A}$ node has two children (inner nodes): $\mathsf{B}$ and the only site
+in this bigraph, labelled by the number $0$.
 
@@
 
-% TODO: mention we will be using bigraphs with sharing and we recall some
-% definitions from TCS paper
 \begin{definition}[concrete place graph with sharing]
@@
 
-% TODO: for the same D_i - not clear
-% TODO: minimal example showing normalisation
 \begin{definition}[probabilistic reaction rule]
@@
   ground probabilistic reaction rules, where for each $r_i$, there exists a
-  bigraph $D_i$ such that $g = D_i \circ r_i$. Let $S = \{ (r_i, r'_i, p_i) \mid
-  g' = D_i \circ r'_i \}$ (for the same $D_i$), and
+  bigraph $D(r_i)$ such that $g = D(r_i) \circ r_i$. Let $S = \{ (r_i, r'_i, p_i) \mid g' = D(r_i) \circ r'_i \}$, and
   \[ s = \sum_{i=1}^n p_i. \]
@@
 
+TODO: minimal example showing normalisation
+
 \subsection{Nondeterministic BRS}
 
+%The next step towards...
 % TODO: intro explaining how we are further generalising the extensions defined
@@
   reaction rule, and $a \in A$ is an action. We also define a \emph{reaction
-    reward function} $r : A \to \mathbb{R}$ that assigns a reward or cost to
+    reward function} $\rho : A \to \mathbb{R}$ that assigns a reward or cost to
   each action.
@@
 
-% TODO: D_i not clear
-% TODO: different symbol for reward
 \begin{definition}[nondeterministic bigraphical reactive system (NBRS)]
@@
   p_i) \}_{i=1}^n$ a set of ground nondeterministic reaction rules with action
-  $a$, where for each $r_i$, there exists a bigraph $D_i$ such that $g =
-  D_i \circ r_i$. Let $S = \{ (r_i, r'_i, a, p_i) \mid g' = D_i \circ r'_i \}$
-  (for the same $D_i$), and
+  $a$, where for each $r_i$, there exists a bigraph $D(r_i)$ such that $g =
+  D(r_i) \circ r_i$. Let $S = \{ (r_i, r'_i, a, p_i) \mid g' = D(r_i) \circ r'_i
+  \}$, and
   \[ s = \sum_{i=1}^n p_i. \]
   Then the reaction relation for action $a$ is defined as
-  \[ g \xrightarrowrhd[r(a)]{p}_{a} g' \text{ iff } S \ne \emptyset, \]
+  \[ g \xrightarrowrhd[\rho(a)]{p}_{a} g' \text{ iff } S \ne \emptyset, \]
   where
@@
 
-% TODO: minimal example, possible the same one as below
+TODO: minimal example, possibly the same one as below.
 
 \section{Implementation}
-
-% TODO: we extend BigraphER
-% TODO: describe the new syntactical constructs using the example
-% TODO: what's the reward of action b?
 
@@
 \texttt{\textbf{action} actionName} and \texttt{\textbf{end}}. Rewards can be
-added to actions simply by inserting an integer enclosed in squared brackets
+added to actions simply by inserting an integer enclosed in square brackets
 after the action name (e.g. \texttt{\textbf{action} b[1]}). Lastly, predicate
@@
 
-\subsection{Front end}
+\subsection{Front End}
 
@@
 behaviour and explore topics such as tracking visited locations and uncertainty
-about the topology.
-
-% TODO: the agent is simply modelled as an atomic node as the focus of this case
-% study is on its movements across a grid. More complex models are possible
-% by...
+about the topology. In both cases the agent is simply modelled as an single
+node, as the focus of this case study is on its movement. More complex models
+are possible by considering which direction the agent is facing
+\cite{koenig1998xavier} or adding extra state to the agent such as limited
+battery life or high/lower power sensors \cite{dblp:conf/nfm/giaquintahimn18}.
 
@@
 
-% TODO: taking advantage of the hierarchical structure of bigraphs
-
 Our second model explores two important concepts in modelling the topology of
@@
 whenever we discuss one space nested inside another, we will refer to the inner
-space as the \emph{room}. While nesting has been modelled using bigraphs before
+space as the \emph{room}. As bigraphs possess their own node nesting, this makes
+bigraphical representations of these spaces more intuitive and easier to manage
+than, say, a vector of numbers, each of which is assigned a particular meaning.
+While nesting has been modelled using bigraphs before
 \cite{DBLP:conf/giscience/WaltonW12}, our approach models each room not as a
@@
 
-% TODO: limitation of a single entrance/exit per cell, can a room have multiple
-% doors (doesn't make sense for this conceptualisation of the problem)?
+\section{Discussion}
 
-% TODO: state diagrams (and statistics about them)
-% TODO: numerical analysis (or ideas)
-% TODO: discussion section
-% TODO: what are the adtantages of using NBRS?
-% TODO: limitations
-% TODO: difficulties
+TODO (possibly): state transition diagrams and statistics about the number of
+states, etc.
+TODO: quantitative analysis with PRISM (need good nontrivial examples)
+
+\begin{itemize}
+\item LIMITATIONS
+  \begin{itemize}
+  \item no easy way to change probabilities depending on the state
+  \item each room only has a single entrance/exit (could be fixed via
+    bigraphs with sharing)
+  \item can't implement everything you can think of: no way to check for set
+    membership, limited support for representing numbers (adding/subtracting $n$
+    has to be a separate reaction rule for each $n$)
+  \end{itemize}
+\item EXTENSIONS
+  \begin{itemize}
+  \item discovery of spaces independent of room structure (no specific ideas
+    yet, but could be very nice)
+  \item there's no good reason why rewards are assigned to actions rather than
+    reaction rules
+  \item multiple agents
+  \item uncertainty in actions (like in Artificial Intelligence: A Modern
+    Approach)
+  \end{itemize}
+\item ADVANTAGES
+  \begin{itemize}
+  \item less code than with PRISM
+  \item more visual and intuitive, represents the modelled situation in a more
+    straightforward way
+  \item rewards and transition rules can be generated with a higher degree of
+    automation (considering a specific property of a state, rather than listing
+    all states that satisfy that property)
+  \item more flexible in changing the size of the grid
+  \item can be easily extended to more than four directions
+  \end{itemize}
+\end{itemize}
 
 \section{Conclusion}
-
-% TODO advantages: more visual/realistic than a vector of numbers, rewards and
-% transition rules can be generated with a higher degree of automation, less
-% code, more flexible (changing size of the grid); disadvantages: constant
-% probability (without hacking)
-% Extensions: multiple agents (nice), uncertainty in actions (easy), rotations
-% (pomdp paper, easy), not limited to four directions
 

### 2018-08-15 paper.tex
PBRS example

@@
 \usepackage{phaistos}
+\usepackage{subcaption}
 
@@
   ground probabilistic reaction rules, where for each $r_i$, there exists a
-  bigraph $D(r_i)$ such that $g = D(r_i) \circ r_i$. Let $S = \{ (r_i, r'_i, p_i) \mid g' = D(r_i) \circ r'_i \}$, and
+  bigraph $D(r_i)$ such that $g = D(r_i) \circ r_i$. Let $S = \{ (r_i, r'_i,
+  p_i) \mid g' = D(r_i) \circ r'_i \}$, and
   \[ s = \sum_{i=1}^n p_i. \]
@@
 
-TODO: minimal example showing normalisation
+\begin{example}
+  Consider a simple PBRS, where the initial state $g_0$ has an \texttt{Agent}
+  and two \texttt{Locations}, each of which is holding an \texttt{Object} (see
+  Fig. \ref{pbrs_initial}), and a single reaction rule with probability $1$ that
+  takes an \texttt{Object} from a \texttt{Location} and transfers it to the
+  \texttt{Agent} (see Fig. \ref{pbrs_rule}). Then, since regions $1$ and $2$ are
+  not treated as isomorphic, the reaction rule can be applied in two ways,
+  resulting in two different subsequent states in Fig. \ref{pbrs_next_states},
+  $g_1$ and $g_2$. Thus, we have two ground probabilistic reaction rules ($n =
+  2$) with $p_1 = p_2 = 1$ and $s = 2$. Let $g' = g_1$. Then $|S| = 1$, and
+  \[ g_0 \xrightarrowrhd{0.5}_{\mathcal{R}} g_1, \]
+  since
+  \[ 0.5 = \frac{1}{2} \sum_{(r, r', 1) \in S} 1. \]
+  Similarly,
+  \[ g_0 \xrightarrowrhd{0.5}_{\mathcal{R}} g_2. \]
+\end{example}
+
+\begin{figure}
+  \centering
+  \includegraphics{models/pbrs_example/initial.pdf}
+  \caption{The initial state.}
+  \label{pbrs_initial}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{minipage}{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{models/pbrs_example/take_lhs.pdf}
+  \end{minipage}
+  $\longrightdoublearrowRHD$
+  \begin{minipage}{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{models/pbrs_example/take_rhs.pdf}
+  \end{minipage}
+  \caption{The reaction rule to take an \texttt{Object} from a
+    \texttt{Location}.}
+  \label{pbrs_rule}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{models/pbrs_example/1.pdf}
+    \caption{$g_1$}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{0.45\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{models/pbrs_example/2.pdf}
+    \caption{$g_2$}
+  \end{subfigure}
+  \caption{Two possible next states, depending on which \texttt{Object} is
+    taken.}
+  \label{pbrs_next_states}
+\end{figure}
 

### 2018-08-15 paper.tex
Introduction

@@
 \providecommand\longrightarrowrhd{\relbar\joinrel\relbar\joinrel\mathrel\rhd}
-\providecommand\longrightdoublearrowRHD{\mathrel\LHD\joinrel\relbar\joinrel\relbar\joinrel\mathrel\RHD}
+\providecommand\longdoublearrowRHD{\mathrel\LHD\joinrel\relbar\joinrel\relbar\joinrel\mathrel\RHD}
 
@@
 \providecommand*\xrightarrowrhd[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longrightarrowrhd}{#1}{#2}}
+\providecommand*\xdoublearrowRHD[2][]{\ext@arrow 0055{\arrowfill@\relbar\relbar\longdoublearrowRHD}{#1}{#2}}
+
 \makeatother
@@
 
-TODO: introduction to bigraphs and everything else
-%Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
-%universal formalism for modelling interacting systems that evolve in time and
-%space.
+Bigraphical reactive systems (BRS) \cite{DBLP:books/daglib/0022395} are a
+universal formalism for modelling interacting systems that evolve in time and
+space. They consist of bigraphs and reaction rules. Bigraphs are algebraic terms
+for modelling agents, connections, and their placement within each other, while
+reaction rules specify how one bigraph can evolve into another. BRSs have
+been used to represent a diverse range of phenomena: games
+\cite{DBLP:journals/tochi/BenfordCRS16}, network management
+\cite{DBLP:journals/scp/CalderKSS14}, protocols
+\cite{DBLP:journals/fac/CalderS14}, biological processes
+\cite{DBLP:journals/entcs/KrivineMT08}, real world environments
+\cite{DBLP:conf/giscience/WaltonW12}, etc. Extending BRSs with probabilities,
+uncertainty, and rewards allows us to model an even wider range of processes and
+systems, examples of which will be given in Section \ref{case_study}. In this
+section we introduce and define the main concepts built upon in the remainder of
+paper: Markov decision processes and BRSs.
 
@@
   \end{minipage}
-  $\longrightdoublearrowRHD$
+  $\xrightarrowRHD{1}$
   \begin{minipage}{0.45\textwidth}
@@
 
-\section{A Case Study in Autonomous Agents}
+\section{A Case Study in Autonomous Agents} \label{case_study}
 
@@
   \end{minipage}
-  $\longrightdoublearrowRHD$
+  $\xdoublearrowRHD{1}$
   \begin{minipage}{0.45\textwidth}

### 2018-08-15 paper.tex
And another example

@@
   delivered, and the process stops. But sometimes a message fails to deliver, in
-  which case the process has to restart. See Fig. \ref{first_mdp} for a
+  which case the process has to restart. See Fig.~\ref{first_mdp} for a
   visualisation of $M$.
@@
   and two \texttt{Locations}, each of which is holding an \texttt{Object} (see
-  Fig. \ref{pbrs_initial}), and a single reaction rule with probability $1$ that
+  Fig.~\ref{pbrs_initial}), and a single reaction rule with probability $1$ that
   takes an \texttt{Object} from a \texttt{Location} and transfers it to the
-  \texttt{Agent} (see Fig. \ref{pbrs_rule}). Then, since regions $1$ and $2$ are
+  \texttt{Agent} (see Fig.~\ref{pbrs_rule}). Then, since regions $1$ and $2$ are
   not treated as isomorphic, the reaction rule can be applied in two ways,
-  resulting in two different subsequent states in Fig. \ref{pbrs_next_states},
+  resulting in two different subsequent states in Fig.~\ref{pbrs_next_states},
   $g_1$ and $g_2$. Thus, we have two ground probabilistic reaction rules ($n =
@@
   Then the reaction relation for action $a$ is defined as
-  \[ g \xrightarrowrhd[\rho(a)]{p}_{a} g' \text{ iff } S \ne \emptyset, \]
+  \[ g \xrightarrowrhd[\rho(a)]{p}_a g' \text{ iff } S \ne \emptyset, \]
   where
@@
 
-TODO: minimal example, possibly the same one as below.
-
-\section{Implementation}
-
-The described extensions have been implemented in an open-source tool for BRSs
-BigraphER \cite{DBLP:conf/cav/SevegnaniC16}. We refer the interested reader to
-the paper on BigraphER \cite{DBLP:conf/cav/SevegnaniC16}, the related PhD thesis
-\cite{DBLP:phd/ethos/Sevegnani12}, and online
-resources\footnote{\url{http://www.dcs.gla.ac.uk/~michele/bigrapher.html}} for
-further information on the syntax and capabilities of the software. In this
-section we will introduce the new features of BigraphER by using a simple MDP as
-an example.
-
 \begin{example} \label{example}
-  Consider an MDP $(S, \overline{s}, A, P, L)$, where $S = \{ s_0, s_1, s_2, s_3
-  \}$, $\overline{s} = s_0$, $A = \{ a, b, c \}$, and $P, L$ are defined as
+  Consider an MDP $(S, \overline{s}, A, P, L)$, where $S = \{ s_0, s_1, s_2,
+  s_3 \}$, $\overline{s} = s_0$, $A = \{ a, b, c \}$, and $P, L$ are defined as
   follows:
@@
   else.
+
+  Let $s_0, s_1, s_2, s_3$ also denote the bigraphs representing these states.
+  Then we have the following reaction relations:
+  \begin{align*}
+    s_0 &\xrightarrowrhd{1}_a s_1, & s_1 &\xrightarrowrhd[1]{0.7}_b s_0, & s_1 &\xrightarrowrhd[1]{0.3}_b s_1, & s_1 &\xrightarrowrhd{0.5}_c s_2, & \\
+    s_1 &\xrightarrowrhd{0.5}_c s_3, & s_2 &\xrightarrowrhd{1}_a s_2, & s_3 &\xrightarrowrhd{1}_a s_3,
+  \end{align*}
+  where zero rewards have been omitted for clarity.
 \end{example}
+
+\section{Implementation}
+
+The described extensions have been implemented in an open-source tool for BRSs
+BigraphER \cite{DBLP:conf/cav/SevegnaniC16}. We refer the interested reader to
+the paper on BigraphER \cite{DBLP:conf/cav/SevegnaniC16}, the related PhD thesis
+\cite{DBLP:phd/ethos/Sevegnani12}, and online
+resources\footnote{\url{http://www.dcs.gla.ac.uk/~michele/bigrapher.html}} for
+further information on the syntax and capabilities of the software. In this
+section we will introduce the new features of BigraphER by turning Example
+\ref{example} into an NBRS.
 
@@
 
-The MDP can be represented as an NBRS with BigraphER code in
-Listing~\ref{example_listing}. More specifically, reaction rule probabilities
-are represented as floating-point numbers inside the arrows (e.g.
-\texttt{-[0.7]->}), each action encompasses its reaction rules with
+The full BigraphER code for this example is in Listing~\ref{example_listing}.
+Reaction rule probabilities are represented as floating-point numbers inside the
+arrows (e.g. \texttt{-[0.7]->}), each action encompasses its reaction rules with
 \texttt{\textbf{action} actionName} and \texttt{\textbf{end}}. Rewards can be
@@
 displays the graphical representation of all bigraphs and reaction rules defined
-in that cell (see Fig. \ref{interface} for an example). The generated images are
+in that cell (see Fig.~\ref{interface} for an example). The generated images are
 stored in a local directory \texttt{jupyter-images/}. The kernel also supports a
@@
   \item[\texttt{\%states}] produces a state transition diagram (similar to the
-    one in Fig. \ref{example_ts}). Mousing over a state shows what that
+    one in Fig.~\ref{example_ts}). Mousing over a state shows what that
     state looks like as a bigraph.
@@
 In order to implement nesting, we put a \texttt{Node} (representing a room)
-inside a \texttt{Cell}, which has the ``door'' to that room (see Fig.
-\ref{agent2_nesting}). The \texttt{Node} can have its own collection of
+inside a \texttt{Cell}, which has the ``door'' to that room (see
+Fig.~\ref{agent2_nesting}). The \texttt{Node} can have its own collection of
 \texttt{Cell}s, describing the topology of the room. One of these \texttt{Cell}s
@@
 top two \texttt{Cell}s are not linked, possibly forcing the agent to choose a
-different path (see Fig. \ref{agent2_map}). Finally, we have four actions, each
+different path (see Fig.~\ref{agent2_map}). Finally, we have four actions, each
 with a single reaction rule with probability $1$, corresponding to the four

### 2018-08-15 paper.tex
OKish state again

@@
 
-\begin{definition}[solid bigraph]
+\begin{definition}[solid bigraph] \label{solid}
   A bigraph is \emph{solid} if these conditions hold:
@@
 
-% TODO: why we limit reaction rules to solid (stochastic bigraphs paper)
 \begin{definition}[reaction rule] \label{reaction_rule}
@@
 \end{definition}
+
+The condition that $R$ must be solid ensures that the ground reaction rule is
+unique for a given pair of $g$ and $D$.
 
@@
 
-%The next step towards...
-% TODO: intro explaining how we are further generalising the extensions defined
-% above
+We extend PBRS even further by adding rewards to both reaction rules and
+predicates, and grouping reaction rules into actions. This allows us to
+represent any MDP as a nondeterministic BRS. This can be done either trivially
+(see Example \ref{example}) or in a more efficient manner, by treating each
+bigraph as a complex system, only parts of which are relevant to any given
+reaction rule or predicate.
 
@@
 
+Food for thought: what models have efficient (i.e. polynomial in size)
+representation as BRSs? Can we define complexity classes (easy for everyone,
+easy for bigraphs but not for everyone, hard for everyone)?
+
 \bibliographystyle{splncs04}

### 2018-08-15 paper.tex
PRISM for Agent 1

@@
 \lstinputlisting[caption=Controls., captionpos=b, language=Big,
-label=agent1_controls, firstline=3, lastline=14]{models/agent1.big}
+label=agent1_controls, firstline=3, lastline=14]{models/agent1/agent.big}
 
@@
 language=Big, label=agent1_code, firstline=16,
-lastline=30]{models/agent1.big}
+lastline=30]{models/agent1/agent.big}
 
@@
 language=Big, label=agent1_north, firstline=88,
-lastline=117]{models/agent1.big}
+lastline=117]{models/agent1/agent.big}
 
@@
 objects is acquired., captionpos=b, language=Big, label=agent1_home,
-firstline=186, lastline=189]{models/agent1.big}
+firstline=186, lastline=189]{models/agent1/agent.big}
 

### 2018-08-16 paper.tex
Agent 1 part of PRISM

@@
 \usepackage{subcaption}
+\usepackage{booktabs}
 
@@
 \title{Nondeterministic Bigraphical Reactive Systems for Markov Decision
-  Processes\thanks{Supported by organization x.}}
+  Processes\thanks{Supported by an EPSRC Vacation Scholarship.}}
 \titlerunning{Nondeterministic BRSs for MDPs}
@@
 
+\subsection{Exporting to PRISM}
+
+% TODO: need to cite something about the syntax, logic, etc.
+Now that we have two models defined in BigraphER, we will briefly show how they
+can be exported and used for quantitative analysis with PRISM.
+
+For our first model, we set the probability of finding an object to $p = 0.5$
+and keep the same $2 \times 2$ grid. We ask PRISM to compute \texttt{Pmax=? [ F
+  "goal" ]}, i.e., the maximum probability of reaching the goal. Recall that the
+goal is to collect $n$ objects. We vary $n$ from $1$ to $3$ (as collecting $0$
+objects is trivial, and collecting more than $3$ is impossible given the size of
+the grid) and show the resulting probabilities in Table \ref{agent1_prism}. The
+reader is welcome to check that the numbers are as expected.
+
+\begin{table}
+  \centering
+  \begin{tabular}{l r r r}
+    \toprule
+    $n$ & \tablenum{1} & \tablenum{2} & \tablenum{3} \\
+    \texttt{Pmax} & \tablenum{0.875} & \tablenum{0.5} & \tablenum{0.125} \\
+    \bottomrule
+  \end{tabular}
+  \caption{The maximum probability of collecting $n$ objects in a $2 \times 2$
+    grid, where the probability of finding an object is \num{0.5} when visiting
+    a cell for the first time.}
+  \label{agent1_prism}
+\end{table}
+
+For the second model..
+
 \section{Discussion}
@@
 states, etc.
-TODO: quantitative analysis with PRISM (need good nontrivial examples)
 

### 2018-08-16 paper.tex
PRISM section (kind of) complete

@@
 \usepackage{amsfonts}
+\usepackage{amssymb}
 \usepackage{mathtools}
@@
     \draw (3, 2) -- (3, 0) -- (1, 0) -- (1, 2) -- (0, 2) -- (0, 3) -- (3, 3) -- (3, 2) -- (2, 2);
-    % the probabilistic wall
+    % probabilistic wall
     \draw[red,ultra thick,dashed] (2, 2) -- (2, 1);
-    % the background grid
+    % background grid
     \draw[gray,very thin] (1, 3) -- (1, 2);
@@
     \draw[gray,very thin] (2, 1) -- (2, 0);
-    % the agent
+    % agent
     \node at (0.5, 2.3) {\PHchild};
-    % the door
+    % door
     \draw[dotted] (1.25,2) arc (180:270:0.5cm);
@@
     \draw (1.75, 2) -- (2, 2);
+    % target
+    \node at (2.5, 1.5) {$\bigstar$};
   \end{tikzpicture}
@@
     connecting the middle cell of the top row with a $2 \times 2$ room below.
-    The dashed wall exists with probability $1-p$.}
+    The dashed wall exists with probability $p$. The star denotes the goal
+    location used in Section \ref{prism_section}.}
   \label{agent2_map}
@@
 other action can take place, the two reaction rules in Listing~\ref{agent2_room}
-are put on a higher priority class. With probability $p$, the generated room has
-each \texttt{Cell} linked to its two neighbours; and with probability $1-p$, the
-top two \texttt{Cell}s are not linked, possibly forcing the agent to choose a
-different path (see Fig.~\ref{agent2_map}). Finally, we have four actions, each
-with a single reaction rule with probability $1$, corresponding to the four
+are put on a higher priority class. With probability $1-p$, the generated room
+has each \texttt{Cell} linked to its two neighbours; and with probability $p$,
+the top two \texttt{Cell}s are not linked, possibly forcing the agent to choose
+a different path (see Fig.~\ref{agent2_map}). Finally, we have four actions,
+each with a single reaction rule with probability $1$, corresponding to the four
 possible directions of travel. The reaction rules are very similar to those of
@@
 
-\subsection{Exporting to PRISM}
+\subsection{Exporting to PRISM} \label{prism_section}
 
-% TODO: need to cite something about the syntax, logic, etc.
 Now that we have two models defined in BigraphER, we will briefly show how they
-can be exported and used for quantitative analysis with PRISM.
+can be exported and used for quantitative analysis with PRISM. More information
+about the syntax and capabilities of PRISM properties can be found in the PRISM
+manual\footnote{\url{http://www.prismmodelchecker.org/manual/PropertySpecification/Introduction}}.
 
@@
 the grid) and show the resulting probabilities in Table \ref{agent1_prism}. The
-reader is welcome to check that the numbers are as expected.
+reader is invited to check that the numbers are as expected.
 
@@
 
-For the second model..
+For the second model, we set the probability of having an extra wall in the
+generated room to $p = 0.9$ and add a new atomic control called \texttt{Goal} to
+denote a target location for the agent to move to. We modify the \texttt{room}
+action to place the goal at the position marked by the star in
+Fig.~\ref{agent2_map}. In order to count ``time'' (i.e. how many transitions are
+taken), we add a predicate satisfied by every state (\texttt{Agent}) with a
+reward of $1$. We also define a predicate \texttt{\textbf{big} goal =
+  Cell\{x\}.(Agent | Goal | id)} that checks if the agent has reached the target
+location. With these modifications in place, we can ask PRISM to compute
+\texttt{Rmin=? [ F "goal" ]}, i.e., the minimum number of transitions needed to
+arrive at the target location. The answer given by PRISM is \num{5.8}, and we
+can check that this is indeed the correct answer: the agent takes $4$ steps
+\SI{10}{\percent} of the time and $6$ steps when it needs to move around the
+wall (remember to include the transition for generating the room).
 
@@
     has to be a separate reaction rule for each $n$)
+  \item PRISM doesn't support importing transition rewards, positive and
+    negative rewards at the same time, importing SMGs.
   \end{itemize}

### 2018-08-18 paper.tex
The paper is in a submittable state for the first time!

@@
 of the \texttt{\textbf{begin nbrs}}---\texttt{\textbf{end}} block (e.g.
-\texttt{\textbf{preds} = \{heads[3]\};}).
+\texttt{\textbf{preds} = \{heads[3]\}}).
 
@@
 
-\subsection{Collecting Objects in a Grid}
+\subsection{Collecting Objects in a Grid} \label{first_agent_section}
 
@@
 Now that we have two models defined in BigraphER, we will briefly show how they
-can be exported and used for quantitative analysis with PRISM. More information
-about the syntax and capabilities of PRISM properties can be found in the PRISM
+can be exported and used for quantitative analysis with PRISM. Suppose a model
+is in a file called \texttt{agent.big}. Then, in order to export labels, the
+transition matrix, and state rewards, one would call
+\[ \texttt{bigrapher full -l
+    agent.csl -p agent.tra -r agent.rews agent.big}. \]
+The \texttt{agent.csl} file can then be augmented with the desired
+\emph{properties} to check or compute, and run with PRISM with the command
+\begin{multline*}
+\texttt{prism -importtrans agent.tra -importstaterewards agent.rews
+  \textbackslash} \\ \texttt{agent.csl}.
+\end{multline*}
+More information about the syntax and capabilities of PRISM properties can be
+found in the PRISM
 manual\footnote{\url{http://www.prismmodelchecker.org/manual/PropertySpecification/Introduction}}.
@@
 
-TODO (possibly): state transition diagrams and statistics about the number of
-states, etc.
+%TODO (possibly): state transition diagrams and statistics about the number of
+%states, etc.
 
-\begin{itemize}
-\item LIMITATIONS
-  \begin{itemize}
-  \item no easy way to change probabilities depending on the state
-  \item each room only has a single entrance/exit (could be fixed via
-    bigraphs with sharing)
-  \item can't implement everything you can think of: no way to check for set
-    membership, limited support for representing numbers (adding/subtracting $n$
-    has to be a separate reaction rule for each $n$)
-  \item PRISM doesn't support importing transition rewards, positive and
-    negative rewards at the same time, importing SMGs.
-  \end{itemize}
-\item EXTENSIONS
-  \begin{itemize}
-  \item discovery of spaces independent of room structure (no specific ideas
-    yet, but could be very nice)
-  \item there's no good reason why rewards are assigned to actions rather than
-    reaction rules
-  \item multiple agents
-  \item uncertainty in actions (like in Artificial Intelligence: A Modern
-    Approach)
-  \end{itemize}
-\item ADVANTAGES
-  \begin{itemize}
-  \item less code than with PRISM
-  \item more visual and intuitive, represents the modelled situation in a more
-    straightforward way
-  \item rewards and transition rules can be generated with a higher degree of
-    automation (considering a specific property of a state, rather than listing
-    all states that satisfy that property)
-  \item more flexible in changing the size of the grid
-  \item can be easily extended to more than four directions
-  \end{itemize}
-\end{itemize}
+While using bigraphs to model movement did allow us to achieve some results
+quite easily as well as to explore ideas not easily expressed otherwise, we have
+to acknowledge some limitation that we have encountered throughout the process.
 
-\section{Conclusion}
+First, the probability assigned to a reaction rule stays constant. The only way
+it can be changed is by manipulating the number of rules applicable to a given
+bigraph.
 
-Food for thought: what models have efficient (i.e. polynomial in size)
-representation as BRSs? Can we define complexity classes (easy for everyone,
-easy for bigraphs but not for everyone, hard for everyone)?
+Second, there are some quite elementary concepts that cannot be
+expressed in terms of bigraphs and reaction rules without significant
+limitations or hindrances (or at all). For example, suppose we represent two
+numbers $m, n \in \mathbb{N}$ in our bigraph and wish to have a reaction rule
+that replaces $m$ with $m + n$. The only way to do that is by having a separate
+reaction rule for each possible value of $n$. Another example of a simple
+concept with no bigraphical representation is checking whether an element is in
+a set, where both the element and the set have some representations in a
+bigraph.
+
+Third, there are significant limitations with regards to PRISM integration.
+While we implemented the functionality to export transition rewards based on how
+PRISM exports them, to the author's surprise, PRISM does not support importing
+them (yet). In addition, while it is trivial to support both positive and
+negative numbers as rewards/costs, for PRISM it is a completely different
+problem---one that is not solved yet \cite{DBLP:conf/tacas/0001BCDDKM016}. Also,
+the format for exporting the data to PRISM limits the kind of properties that
+can be computed or checked: while PRISM supports having several rewards and
+referring to each of them as needed, there is no way to define several rewards
+within the plain text formats provided. Finally, while it would be trivial to
+extend the nondeterminism to different ``players'' making different decisions
+(modelling stochastic multiplayer games \cite{DBLP:phd/dnb/Ummels11}), and PRISM
+has an extension that supports such scenarios \cite{DBLP:conf/tacas/ChenFKPS13},
+there is no way to import player labels together with the transition system.
+
+On the other hand, choosing to model with bigraphs rather than, e.g., the
+PRISM language has some clear advantages as well. First, our example model in
+Section \ref{first_agent_section} resulted in significantly less code than a
+similar model in PRISM \cite{dblp:conf/nfm/giaquintahimn18}. Second, our models
+can be much easier to modify: in order to change or extend the grid in some way
+one only needs to change a single bigraph. Similarly, changing how the movement
+of the agent is represented (the number of directions of movement, tracking
+rotations separately from moving forward, adding a probability of accidentally
+moving the wrong way, etc.) results in several simple changes. Third, bigraphs
+come with a visual representation as well as constructs such as nesting and
+linking, allowing for a richer and more intuitive way to represent many modelled
+situations.
+
+\section{Conclusions and Future Work}
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    % outer walls
+    \draw (4, 2) -- (4, 0) -- (1, 0) -- (1, 2) -- (0, 2) -- (0, 3) -- (4, 3) -- (4, 2);
+    % inner walls
+    \draw (2, 2) -- (3, 2) -- (3, 1);
+    %\draw[red,ultra thick,dashed] (2, 2) -- (2, 1);
+    % door 1
+    \draw[dotted] (1.25,2) arc (180:270:0.5cm);
+    \draw[brown,ultra thick] (1.75,1.5) -- (1.75,2) node[right,  near start]{};
+    \draw (1, 2) -- (1.25, 2);
+    \draw (1.75, 2) -- (2, 2);
+    % door 2
+    \draw[dotted] (3.25,2) arc (180:270:0.5cm);
+    \draw[brown,ultra thick] (3.75,1.5) -- (3.75,2) node[right,  near start]{};
+    \draw (3, 2) -- (3.25, 2);
+    \draw (3.75, 2) -- (4, 2);
+    % door 3
+    \draw[dotted] (3, 0.75) arc (90:180:0.5cm);
+    \draw[brown,ultra thick] (2.5, 0.25) -- (3, 0.25) node[right,  near start]{};
+    \draw (3, 0.25) -- (3, 0);
+    \draw (3, 0.75) -- (3, 1);
+    % background grid
+    \draw[gray,very thin] (1, 3) -- (1, 2);
+    \draw[gray,very thin] (2, 3) -- (2, 0);
+    \draw[gray,very thin] (3, 3) -- (3, 2);
+    \draw[gray,very thin] (1, 1) -- (4, 1);
+  \end{tikzpicture}
+  \caption{An example map where both rooms have two doors.}
+  \label{multiple_doors}
+\end{figure}
+
+In this paper we have proposed a way to extend BRSs with probabilities and
+nondeterminism, allowing them to represent any MDP. We have presented a new
+interface for the development and visualisation of BRSs and provided two
+example models for autonomous agents, finding more efficient representations for
+models that already exist as well as tackling new challenges.
+
+% TODO: code for representing the map
+% TODO: what if a door to a room is locked (don't remove the room itself)
+Our second example in particular has introduced two new directions for modelling
+space that have not been explored in full yet. First, while it is often useful
+to think of one space as nested inside another, sometimes a room might have
+several doors: one or two to a corridor, and one to an adjacent room (see, e.g.,
+Fig. \ref{multiple_doors}). The model could support this by using the sharing
+part of bigraphs with sharing\footnote{While our definitions are based on this
+  extension, the additional functionality was not used.}, i.e., have the room be
+inside both a \texttt{Cell} in the corridor and a \texttt{Cell} of another room.
+Second, the model glues the discovery of the structure of a room together with
+being near the door: once the agent visits the \texttt{Cell} encompassing the
+room, it immediately discovers what is inside it. It would improve the model
+significantly to have discovery as a completely separate process, where the
+creator of the map has full control over when a substructure is discovered.
+
+Finally, one ought to note that a bigraphical representation can often be
+asymptotically more compact than a full MDP or discrete-time Markov chain and
+sometimes even than a PRISM description of the same situation (until the BRS is
+expanded into its full transition system, that is). This raises an interesting
+question: can we define complexity classes of models, paying particular
+attention to the MDPs that have an exponential number of states, but can be
+represented in a polynomial number of bigraphs and reaction rules? Which of
+these models do not have a PRISM representation of polynomial size?
 

### 2018-08-23 paper.tex
Presentation: animations

@@
 of which has an inner room.}, captionpos=b, language=Big, label=agent2_initial,
-firstline=15, lastline=19]{models/agent2/agent.big}
+firstline=16, lastline=20]{models/agent2/agent.big}
 
@@
 open or closed.}, captionpos=b, language=Big, label=agent2_room,
-firstline=21, lastline=48]{models/agent2/agent.big}
+firstline=22, lastline=49]{models/agent2/agent.big}
 
 \lstinputlisting[caption={The action of going north.}, captionpos=b,
-language=Big, label=agent2_north, firstline=66,
-lastline=75]{models/agent2/agent.big}
+language=Big, label=agent2_north, firstline=67,
+lastline=76]{models/agent2/agent.big}
 
